\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{hyperref}

\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  citecolor=blue,
  urlcolor=blue
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.45\baselineskip}

\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{assumption}{Assumption}
\newtheorem{remark}{Remark}
\newtheorem{definition}{Definition}

\newcommand{\E}{\mathbb{E}}
\newcommand{\Pp}{\mathbb{P}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\ind}[1]{\mathbf{1}\{#1\}}
\newcommand{\eps}{\varepsilon}
\newcommand{\simplex}{\Delta_K}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calG}{\mathcal{G}}
\newcommand{\calL}{\mathcal{L}}
\newcommand{\what}{\widehat w}
\newcommand{\hvec}{\boldsymbol h}
\newcommand{\cvec}{\boldsymbol c}
\newcommand{\one}{\boldsymbol 1}
\newcommand{\argmin}{\operatorname*{arg\,min}}
\newcommand{\argmax}{\operatorname*{arg\,max}}
\DeclareMathOperator{\Ber}{Bernoulli}

\title{\textbf{Direction 1: Audited Primal--Dual Policy Learning}\\
\large Simultaneous Error Control and Cost Regret}
\author{Draft research direction for Cost-Aware PAC Labeling}
\date{July 13, 2026}

\begin{document}
\maketitle

\begin{abstract}
The current audited online PAC-labeling result controls labeling error but does
not compare expert expenditure with a cost-optimal policy.  This note develops
a candidate conference-paper direction that adds such a comparison.  The main
change is to maintain a distribution over a fixed finite class of threshold
policies in addition to the dual price of error.  Expert deferrals and random
audits provide inverse-probability estimates of every policy's counterfactual
AI loss.  A primal exponential-weights update learns inexpensive policies,
while a projected dual update enforces the error budget.  Under an unknown
i.i.d. data distribution, a fixed policy class, predictable decisions,
independent audits, bounded loss, and a safe expert policy, the procedure has
high-probability error slack and audit-inclusive cost regret of order
$\widetilde O(T^{2/3})$.  A tightened internal error target gives exact control
at the requested level $\eps$.  The result is distribution-free over the class
of i.i.d. distributions, but it is not an arbitrary-sequence guarantee.
\end{abstract}

\section{Problem and policy comparator}

We first specialize to one cheap AI source, matching the real online
experiment in the current project.  At round $t$, the learner observes
non-expert information
\[
  Z_t=(X_t,\widehat Y_t,s_t),
\]
where $\widehat Y_t$ is the AI label and $s_t\in[0,1]$ is a fixed proxy loss or
uncertainty score.  The expert label $Y_t$ is initially hidden.  The bounded AI
loss is
\[
  \ell_t=\ell(Y_t,\widehat Y_t)\in[0,1].
\]
An expert label is correct and costs one; an unaudited AI label has deployment
cost zero.  An audited AI label is corrected to $Y_t$ and therefore also costs
one expert query.

Fix $K\ge2$ and thresholds $\tau_1,\ldots,\tau_{K-1}$ before the online run.  Policy $k$
defers to the expert when $s_t\ge \tau_k$.  Include an always-expert policy as
policy $K$.  Write
\[
  D_t(k)=
  \begin{cases}
    \ind{s_t\ge\tau_k},&k<K,\\
    1,&k=K,
  \end{cases}
\]
and define the counterfactual loss and base deployment cost of policy $k$ by
\begin{equation}
  h_t(k)=(1-D_t(k))\ell_t,
  \qquad
  c_t(k)=D_t(k).
  \label{eq:round-loss-cost}
\end{equation}
Thus $h_t(k)$ is the error that policy $k$ would incur before any audit
correction, and $c_t(k)$ is its ordinary expert-deferral cost.  The vectors
$\hvec_t=(h_t(1),\ldots,h_t(K))$ and
$\cvec_t=(c_t(1),\ldots,c_t(K))$ lie in $[0,1]^K$.

For $w\in\simplex:=\{w\in\R_+^K:\sum_k w(k)=1\}$, let
\begin{equation}
  H(w)=\E[w^\top\hvec_t],
  \qquad
  C(w)=\E[w^\top\cvec_t].
  \label{eq:population-HC}
\end{equation}
The expectation is under the unknown data distribution and the independent
randomization $k\sim w$.  The population comparator is the randomized-policy
linear program
\begin{equation}
  C^\star(\eps)
  =
  \min_{w\in\simplex}\ C(w)
  \quad\text{subject to}\quad
  H(w)\le\eps.
  \label{eq:population-comparator}
\end{equation}
The comparator is fixed and non-clairvoyant: it may know the population but it
never observes $Y_t$ before deciding whether to use AI or the expert.
Randomized mixtures are included because they convexify the cost--error
frontier and permit a small tightening of the error target without a
discontinuous jump in optimal cost.

\section{Assumptions}

The following are a clean sufficient set of assumptions for the first
simultaneous error-and-cost theorem.  They are deliberately stronger than the
assumptions of the current arbitrary-sequence error-only theorem.

\begin{assumption}[Unknown i.i.d. stream]
\label{ass:iid}
The pairs $(Z_t,Y_t)$ are independent and identically distributed according to
an arbitrary unknown distribution $P$.  The AI predictor, proxy score, and
threshold grid are fixed before the stream begins.
\end{assumption}

\begin{assumption}[Bounded loss and a safe action]
\label{ass:safe}
The loss satisfies $0\le\ell_t\le1$.  The always-expert policy $K$ has
$h_t(K)=0$ and $c_t(K)=1$ pointwise.  The requested target satisfies
$\eps\in(0,1)$.
\end{assumption}

\begin{assumption}[Predictability and audit randomization]
\label{ass:predictability}
At the start of round $t$, the policy distribution $w_t$, dual variable
$\lambda_t$, and audit probability are measurable with respect to the past.
The learner samples its policy and chooses AI versus expert using only the past
and current $Z_t$.  If AI is selected, the audit draw is conditionally
independent Bernoulli with its declared probability and is drawn before
observing $Y_t$.
\end{assumption}

\begin{assumption}[Counterfactual observability]
\label{ass:observability}
Whenever an expert label is obtained, the learner can evaluate $h_t(k)$ for
every $k\in[K]$.  In the one-source threshold class this is automatic: each
policy either uses the same AI label, whose loss is then known, or defers and
has loss zero.
\end{assumption}

\begin{remark}[What is not assumed]
No calibration relation such as $s_t=\Pp(\widehat Y_t\ne Y_t\mid Z_t)$ is
required.  A poor score may make the best threshold in the class expensive,
but validity and regret relative to that class remain meaningful.  The i.i.d.
assumption does rule out unrestricted distribution shift and adversarial data
sequences; see Section~\ref{sec:scope}.
\end{remark}

\section{Audited primal--dual policy learner}

Let $\bar\eps\in(0,\eps]$ be an internal error target and let
$\Lambda>0$ be a dual cap.  For the fixed-horizon theorem, take a constant
audit probability
\begin{equation}
  \gamma=T^{-1/3}.
  \label{eq:gamma-choice}
\end{equation}
The probability is constant within a run but vanishes with the horizon.  An
anytime implementation can use a doubling schedule or $p_t\asymp t^{-1/3}$
with adaptive learning rates.

When policy $J_t$ is selected, define its actual deferral decision
$D_t=D_t(J_t)$.  If $D_t=0$, draw $A_t\sim\Ber(\gamma)$; if $D_t=1$, set
$A_t=0$ because the expert is already queried.  The expert-label observation
indicator and its conditional probability are
\begin{equation}
  O_t=D_t+(1-D_t)A_t,
  \qquad
  Q_t=D_t+(1-D_t)\gamma.
  \label{eq:observation-mask}
\end{equation}
Thus $Q_t\in[\gamma,1]$.  The inverse-probability estimate of every policy's
loss is
\begin{equation}
  \widehat h_t(k)
  =
  \frac{O_t}{Q_t}h_t(k),
  \qquad k\in[K].
  \label{eq:ipw-vector}
\end{equation}
When $O_t=0$, the implementation sets the entire vector to zero without
evaluating the hidden loss.

The primal update uses the estimated Lagrangian loss
\begin{equation}
  g_t(k)=c_t(k)+\lambda_t\widehat h_t(k).
  \label{eq:primal-gradient}
\end{equation}
The common term $-\lambda_t\bar\eps$ is omitted because it does not affect the
exponential-weights normalization.  The dual update uses
\begin{equation}
  \widehat v_t=w_t^\top\widehat\hvec_t-\bar\eps.
  \label{eq:dual-gradient}
\end{equation}

\begin{algorithm}[ht]
\caption{Audited primal--dual policy learning}
\label{alg:primal-dual}
\small
\begin{algorithmic}[1]
\Require Horizon $T$; threshold policies $[K]$ including always-expert;
target $\bar\eps$; audit rate $\gamma$; dual cap $\Lambda$; learning rates
$\eta_w,\eta_\lambda$.
\State Initialize $w_1(k)=1/K$ and $\lambda_1=0$.
\For{$t=1,\ldots,T$}
  \State Observe $Z_t=(X_t,\widehat Y_t,s_t)$ and compute
  $\{D_t(k),c_t(k)\}_{k=1}^K$.
  \State Sample $J_t\sim w_t$ and set $D_t=D_t(J_t)$.
  \If{$D_t=1$}
    \State Query the expert, release $\widetilde Y_t=Y_t$, and set
    $A_t=0$, $O_t=Q_t=1$.
  \Else
    \State Draw $A_t\sim\Ber(\gamma)$.
    \If{$A_t=1$}
      \State Query the expert, release the corrected label
      $\widetilde Y_t=Y_t$, and set $O_t=1$, $Q_t=\gamma$.
    \Else
      \State Release $\widetilde Y_t=\widehat Y_t$ and set
      $O_t=0$, $Q_t=\gamma$.
    \EndIf
  \EndIf
  \State Form $\widehat\hvec_t$ by \eqref{eq:ipw-vector}.
  \State Set $g_t(k)=c_t(k)+\lambda_t\widehat h_t(k)$ and update
  \[
    w_{t+1}(k)
    =
    \frac{w_t(k)e^{-\eta_w g_t(k)}}
    {\sum_{j=1}^K w_t(j)e^{-\eta_w g_t(j)}}.
  \]
  \State Set $\widehat v_t=w_t^\top\widehat\hvec_t-\bar\eps$ and update
  \[
    \lambda_{t+1}
    =
    \Pi_{[0,\Lambda]}
    \left(\lambda_t+\eta_\lambda\widehat v_t\right).
  \]
\EndFor
\end{algorithmic}
\end{algorithm}

The counterfactual and final released-label losses of the selected policy are
\begin{equation}
  H_t=h_t(J_t),
  \qquad
  G_t=\ell(Y_t,\widetilde Y_t).
  \label{eq:HG}
\end{equation}
Pointwise, $G_t\le H_t$: expert deferrals have zero loss, and audited AI
mistakes are corrected.  The realized total expert cost is
\begin{equation}
  C_t^{\mathrm{tot}}
  =D_t+(1-D_t)A_t.
  \label{eq:total-cost}
\end{equation}
This counts an audited-and-corrected AI item once, not twice.

\section{Explicit finite-horizon quantities}

The theorem below gives explicit, intentionally conservative constants.  Fix
$\delta\in(0,1)$ and define
\begin{equation}
  x=\log\!\left(\frac{64K}{\delta}\right).
  \label{eq:x-def}
\end{equation}
For $\gamma\in(0,1]$, let
\begin{align}
  V_T
  &:=
  \frac{T}{\gamma}
  +\sqrt{\frac{2Tx}{\gamma^3}}
  +\frac{x}{3\gamma^2},
  \label{eq:VT}\\
  S_w
  &:=2T+2\Lambda^2V_T,
  \qquad
  S_\lambda:=2T+2V_T.
  \label{eq:S-def}
\end{align}
Choose
\begin{align}
  \eta_w
  &:=%
  \min\left\{
    \frac{1}{2(1+\Lambda/\gamma)},
    \sqrt{\frac{2\log K}{S_w}}
  \right\},
  \label{eq:eta-w}\\
  \eta_\lambda
  &:=%
  \frac{\Lambda}{\sqrt{S_\lambda}}.
  \label{eq:eta-lambda}
\end{align}
Define the primal and dual optimization terms
\begin{align}
  R_w
  &:=%
  \frac{\log K}{\eta_w}+\frac{\eta_w}{2}S_w,
  \label{eq:Rw}\\
  R_\lambda
  &:=%
  \frac{\Lambda^2}{2\eta_\lambda}
  +\frac{\eta_\lambda}{2}S_\lambda
  =\Lambda\sqrt{S_\lambda},
  \label{eq:Rlambda}
\end{align}
and the stochastic conversion term
\begin{equation}
  R_{\mathrm{stoch}}
  :=
  2\sqrt{2Tx}
  +2\Lambda\left(
    \sqrt{\frac{2Tx}{\gamma}}+\frac{x}{3\gamma}
  \right).
  \label{eq:Rstoch}
\end{equation}
Finally, set
\begin{equation}
  e_T
  :=
  \frac{R_w+R_\lambda+R_{\mathrm{stoch}}}{T},
  \qquad
  r_T:=\sqrt{\frac{x}{2T}},
  \qquad
  a_T:=\gamma+\sqrt{\frac{2\gamma x}{T}}+\frac{x}{3T}.
  \label{eq:error-terms}
\end{equation}
Here $e_T$ is a population saddle-point error, $r_T$ converts population loss
and cost to the realized stream, and $a_T$ upper-bounds the fraction of extra
AI audits.

\section{Main bounds}

For a working target $b\in(0,1)$, define the population value
\[
  C^\star(b)=\min_{w\in\simplex}\{C(w):H(w)\le b\}.
\]

\begin{theorem}[Simultaneous finite-horizon bounds]
\label{thm:main}
Suppose Assumptions~\ref{ass:iid}--\ref{ass:observability} hold.  Run
Algorithm~\ref{alg:primal-dual} with internal target $\bar\eps\in(0,1)$,
$\gamma\in(0,1]$, and $\Lambda>1/\bar\eps$, using
\eqref{eq:eta-w}--\eqref{eq:eta-lambda}.  Then, with probability at least
$1-\delta$ over the data, policy randomization, and audits,
\begin{align}
  \frac1T\sum_{t=1}^T H_t
  &\le
  \bar\eps
  +\frac{e_T}{\Lambda-1/\bar\eps}
  +r_T,
  \label{eq:main-H}\\
  \frac1T\sum_{t=1}^T G_t
  &\le
  \frac1T\sum_{t=1}^T H_t,
  \label{eq:main-G}\\
  \frac1T\sum_{t=1}^T C_t^{\mathrm{tot}}
  &\le
  C^\star(\bar\eps)+e_T+r_T+a_T.
  \label{eq:main-cost}
\end{align}
Thus the result controls the more demanding counterfactual pre-correction
loss, and its cost comparison includes all expert deferrals and audits.
\end{theorem}

The base theorem has a vanishing error slack.  The next corollary spends this
slack in advance to achieve the requested error level exactly.

\begin{corollary}[Exact control at $\eps$ and regret to $C^\star(\eps)$]
\label{cor:exact}
Set
\begin{equation}
  \Lambda=\frac{4}{\eps},
  \qquad
  \kappa_T=\frac{\eps e_T}{2}+r_T,
  \qquad
  \bar\eps=\eps-\kappa_T.
  \label{eq:tightening}
\end{equation}
Assume $\kappa_T\le\eps/2$.  Then, on the event of
Theorem~\ref{thm:main},
\begin{align}
  \frac1T\sum_{t=1}^T G_t
  &\le
  \frac1T\sum_{t=1}^T H_t
  \le\eps,
  \label{eq:exact-error}\\
  \frac1T\sum_{t=1}^T C_t^{\mathrm{tot}}
  &\le
  C^\star(\eps)
  +e_T+\frac{\kappa_T}{\eps}+r_T+a_T.
  \label{eq:exact-cost}
\end{align}
In particular, for $\gamma=T^{-1/3}$ and fixed
$(\eps,K,\delta)$,
\begin{align}
  \sum_{t=1}^T H_t&\le\eps T,\\
  \sum_{t=1}^T C_t^{\mathrm{tot}}
  &\le
  TC^\star(\eps)+\widetilde O_\eps(T^{2/3}).
  \label{eq:T23-summary}
\end{align}
The notation $\widetilde O_\eps$ hides logarithmic factors in
$K,T,1/\delta$ and constants polynomial in $1/\eps$.
\end{corollary}

\begin{remark}[Why $T^{-1/3}$]
The extra audit cost is approximately $T\gamma$, while the partial-feedback
learning term is approximately $\sqrt{T/\gamma}$.  Balancing these terms gives
$\gamma\asymp T^{-1/3}$ and cumulative order $T^{2/3}$.  A fixed positive
audit rate would instead incur linear audit cost.
\end{remark}

\section{Proofs}

We give all intermediate steps because the distinction between observed,
counterfactual, and released-label loss is central to the result.

\subsection{Unbiased loss estimates and second moments}

Let $\calF_{t-1}$ contain the complete history through round $t-1$.
For analysis, let $\calG_t$ augment $\calF_{t-1}$ with the current data,
selected policy, all current counterfactual losses, and the observation
probability $Q_t$, but not the audit coin when AI is selected.  Conditional on
$\calG_t$, $O_t$ is Bernoulli with mean $Q_t$; on a deferral, this is the
degenerate Bernoulli variable equal to one.

\begin{lemma}[Inverse-probability identities]
\label{lem:ipw}
For every $k\in[K]$,
\begin{align}
  \E[\widehat h_t(k)\mid\calG_t]&=h_t(k),
  \label{eq:ipw-unbiased}\\
  \E[\widehat h_t(k)^2\mid\calG_t]
  &\le\frac{h_t(k)^2}{\gamma}.
  \label{eq:ipw-second}
\end{align}
Moreover,
\begin{align}
  \E[w_t^\top\widehat\hvec_t\mid\calF_{t-1}]&=H(w_t),
  \label{eq:mixture-unbiased}\\
  \E[w_t^\top(\widehat\hvec_t\odot\widehat\hvec_t)mid\calF_{t-1}]
  &\le\frac1\gamma.
  \label{eq:mixture-second}
\end{align}
Here $\odot$ denotes componentwise multiplication.
\end{lemma}

\begin{proof}
Conditional on $\calG_t$, $h_t(k)$ and $Q_t$ are fixed and
$\E[O_t\mid\calG_t]=Q_t$.  Hence
\[
  \E\left[\frac{O_t}{Q_t}h_t(k)\,\middle|\,\calG_t\right]
  =h_t(k).
\]
Because $O_t^2=O_t$ and $Q_t\ge\gamma$,
\[
  \E\left[\left(\frac{O_t}{Q_t}h_t(k)\right)^2
  \middle|\calG_t\right]
  =\frac{h_t(k)^2}{Q_t}
  \le\frac{h_t(k)^2}{\gamma}.
\]
Taking iterated expectations over the current i.i.d. data and selected policy
gives \eqref{eq:mixture-unbiased}.  Summing
\eqref{eq:ipw-second} with weights $w_t(k)$ and using
$0\le h_t(k)\le1$ gives \eqref{eq:mixture-second}.
\end{proof}

The following variance event is what improves the rate over a crude
$1/\gamma$-range analysis.

\begin{lemma}[High-probability quadratic variation]
\label{lem:quadratic}
With probability at least $1-e^{-x}$,
\begin{equation}
  \sum_{t=1}^T
  w_t^\top(\widehat\hvec_t\odot\widehat\hvec_t)
  \le V_T,
  \label{eq:quadratic-event}
\end{equation}
where $V_T$ is defined in \eqref{eq:VT}.  On this event,
\begin{align}
  \sum_{t=1}^T w_t^\top(\boldsymbol g_t\odot\boldsymbol g_t)&\le S_w,
  \label{eq:primal-square}\\
  \sum_{t=1}^T\widehat v_t^2&\le S_\lambda.
  \label{eq:dual-square}
\end{align}
\end{lemma}

\begin{proof}
Set
$X_t=w_t^\top(\widehat\hvec_t\odot\widehat\hvec_t)$.
By Lemma~\ref{lem:ipw},
$\E[X_t\mid\calF_{t-1}]\le1/\gamma$.
Also $0\le X_t\le1/\gamma^2$.  Conditional on $\calG_t$,
$X_t=(O_t/Q_t^2)w_t^\top(\hvec_t\odot\hvec_t)$, so
\[
  \E[X_t^2\mid\calG_t]
  \le\frac{1}{Q_t^3}
  \le\frac{1}{\gamma^3}.
\]
Therefore the martingale differences
$X_t-\E[X_t\mid\calF_{t-1}]$ have increments bounded above by
$1/\gamma^2$ and total conditional variance at most $T/\gamma^3$.
Freedman's inequality gives
\[
  \sum_{t=1}^T X_t
  \le
  \frac{T}{\gamma}
  +\sqrt{\frac{2Tx}{\gamma^3}}
  +\frac{x}{3\gamma^2}
  =V_T.
\]
Next, $(a+b)^2\le2a^2+2b^2$ gives
\[
  g_t(k)^2
  \le2c_t(k)^2+2\Lambda^2\widehat h_t(k)^2.
\]
Summing with weights $w_t(k)$ proves \eqref{eq:primal-square}.
Finally, Jensen's inequality gives
$(w_t^\top\widehat\hvec_t)^2
\le w_t^\top(\widehat\hvec_t\odot\widehat\hvec_t)$, and hence
\[
  \widehat v_t^2
  \le2(w_t^\top\widehat\hvec_t)^2+2\bar\eps^2.
\]
Summation proves \eqref{eq:dual-square}.
\end{proof}

\subsection{Primal and dual regret}

Define the estimated per-round Lagrangian
\begin{equation}
  \widehat F_t(w,\lambda)
  =w^\top\cvec_t+\lambda(w^\top\widehat\hvec_t-\bar\eps).
  \label{eq:estimated-F}
\end{equation}

\begin{lemma}[Estimated saddle regret]
\label{lem:estimated-saddle}
On the event in Lemma~\ref{lem:quadratic}, for every
$u\in\simplex$ and $\lambda\in[0,\Lambda]$,
\begin{equation}
  \sum_{t=1}^T\widehat F_t(w_t,\lambda)
  -\sum_{t=1}^T\widehat F_t(u,\lambda_t)
  \le R_w+R_\lambda.
  \label{eq:estimated-saddle-regret}
\end{equation}
\end{lemma}

\begin{proof}
Because $g_t(k)\ge0$ and
$g_t(k)\le1+\Lambda/\gamma$, the first term in the minimum defining
$\eta_w$ ensures $\eta_wg_t(k)\le1/2$.  The standard exponential-weights
potential argument, using $e^{-z}\le1-z+z^2/2$ for $z\ge0$, gives
\[
  \sum_{t=1}^T w_t^\top\boldsymbol g_t
  -\sum_{t=1}^T u^\top\boldsymbol g_t
  \le
  \frac{\log K}{\eta_w}
  +\frac{\eta_w}{2}
  \sum_{t=1}^T w_t^\top(\boldsymbol g_t\odot\boldsymbol g_t)
  \le R_w.
\]
Since the term $-\lambda_t\bar\eps$ is common to $w_t$ and $u$, this is
equivalently
\[
  \sum_{t=1}^T\widehat F_t(w_t,\lambda_t)
  -\sum_{t=1}^T\widehat F_t(u,\lambda_t)
  \le R_w.
\]

For the projected dual-ascent step, nonexpansiveness of Euclidean projection
implies, for every $\lambda\in[0,\Lambda]$,
\[
  \sum_{t=1}^T(\lambda-\lambda_t)\widehat v_t
  \le
  \frac{\Lambda^2}{2\eta_\lambda}
  +\frac{\eta_\lambda}{2}\sum_{t=1}^T\widehat v_t^2
  \le R_\lambda.
\]
The left side equals
$\sum_t\widehat F_t(w_t,\lambda)
-\sum_t\widehat F_t(w_t,\lambda_t)$.
Adding the primal and dual inequalities proves
\eqref{eq:estimated-saddle-regret}.
\end{proof}

\subsection{From sampled Lagrangians to the population saddle problem}

Define the population Lagrangian
\begin{equation}
  F(w,\lambda)
  =C(w)+\lambda(H(w)-\bar\eps).
  \label{eq:population-F}
\end{equation}

\begin{lemma}[Uniform stochastic conversion]
\label{lem:conversion}
With probability at least $1-8Ke^{-x}$, simultaneously for every
$u\in\simplex$ and $\lambda\in[0,\Lambda]$,
\begin{align}
  \Bigg|
  \sum_{t=1}^T\bigl\{
  \widehat F_t(w_t,\lambda)-F(w_t,\lambda)
  \bigr\}
  \Bigg|
  &\le
  \sqrt{2Tx}
  +\Lambda\left(
    \sqrt{\frac{2Tx}{\gamma}}+\frac{x}{3\gamma}
  \right),
  \label{eq:left-conversion}\\
  \Bigg|
  \sum_{t=1}^T\bigl\{
  \widehat F_t(u,\lambda_t)-F(u,\lambda_t)
  \bigr\}
  \Bigg|
  &\le
  \sqrt{2Tx}
  +\Lambda\left(
    \sqrt{\frac{2Tx}{\gamma}}+\frac{x}{3\gamma}
  \right).
  \label{eq:right-conversion}
\end{align}
\end{lemma}

\begin{proof}
We separate cost and loss.  Because $w_t$ is measurable with respect to the
past and the data are i.i.d.,
$w_t^\top\cvec_t-C(w_t)$ is a bounded martingale difference.  Azuma--Hoeffding
controls its absolute sum by $\sqrt{2Tx}$ except on an event of probability at
most $2e^{-x}$.  For any fixed policy $k$, the same argument controls
$\sum_t(c_t(k)-C(e_k))$.  A union bound over $k$ and linearity in $u$ extend
the result to every $u\in\simplex$.

For loss, Lemma~\ref{lem:ipw} shows that
$w_t^\top\widehat\hvec_t-H(w_t)$ is a martingale difference.  Its increment is
bounded in absolute value by $1/\gamma$, and its conditional variance is at
most $1/\gamma$.  Freedman's inequality therefore gives
\[
  \left|
  \sum_{t=1}^T
  \{w_t^\top\widehat\hvec_t-H(w_t)\}
  \right|
  \le
  \sqrt{\frac{2Tx}{\gamma}}+\frac{x}{3\gamma}
\]
outside an event of probability at most $2e^{-x}$.  Multiplying by any fixed
$\lambda\in[0,\Lambda]$ costs at most a factor $\Lambda$.

For the right side, fix a vertex $e_k$ of the simplex.  The sequence
\[
  \lambda_t\{\widehat h_t(k)-H(e_k)\}
\]
is a martingale difference with absolute increment at most
$\Lambda/\gamma$ and conditional variance at most $\Lambda^2/\gamma$.
Freedman's inequality gives the stated loss bound.  A union bound over $k$ and
linearity in $u$ give the result for every mixture $u$.  Combining the cost and
loss events proves the claim; the displayed failure probability is a
conservative union bound.
\end{proof}

\begin{proposition}[Population saddle gap]
\label{prop:saddle-gap}
Let
\[
  \overline w_T=\frac1T\sum_{t=1}^T w_t,
  \qquad
  \overline\lambda_T=\frac1T\sum_{t=1}^T\lambda_t.
\]
With probability at least $1-\delta/2$,
\begin{equation}
  \max_{\lambda\in[0,\Lambda]}F(\overline w_T,\lambda)
  -\min_{u\in\simplex}F(u,\overline\lambda_T)
  \le e_T.
  \label{eq:population-saddle-gap}
\end{equation}
\end{proposition}

\begin{proof}
Intersect the events of Lemmas~\ref{lem:quadratic} and
\ref{lem:conversion}.  Their total failure probability is below $\delta/2$
under the choice \eqref{eq:x-def}.  Combining
Lemma~\ref{lem:estimated-saddle} with the two conversion bounds gives, for
every $u$ and $\lambda$,
\[
  \sum_{t=1}^T F(w_t,\lambda)
  -\sum_{t=1}^T F(u,\lambda_t)
  \le R_w+R_\lambda+R_{\mathrm{stoch}}.
\]
The population Lagrangian is bilinear, so the left side divided by $T$ equals
$F(\overline w_T,\lambda)-F(u,\overline\lambda_T)$.  Maximizing over
$\lambda$ and minimizing over $u$ proves the proposition.
\end{proof}

\subsection{Exact penalty and separate population bounds}

\begin{lemma}[Safe policy bounds the optimal dual price]
\label{lem:dual-bound}
For any target $b\in(0,1)$, the LP defining $C^\star(b)$ has an optimal dual
price $\lambda^\star_b$ satisfying
\begin{equation}
  0\le\lambda^\star_b\le\frac1b.
  \label{eq:dual-bound}
\end{equation}
\end{lemma}

\begin{proof}
The problem is a finite linear program and is strictly feasible because the
always-expert policy has loss zero.  Strong duality therefore holds.  Its dual
function is
\[
  d_b(\lambda)
  =\min_{w\in\simplex}
  \{C(w)+\lambda(H(w)-b)\}.
\]
Evaluating the inner minimum at the always-expert policy gives
$d_b(\lambda)\le1-\lambda b$.  At a dual optimum,
$C^\star(b)=d_b(\lambda_b^\star)\ge0$, so
$0\le1-\lambda_b^\star b$, proving
$\lambda_b^\star\le1/b$.
\end{proof}

\begin{lemma}[Saddle gap implies cost and feasibility]
\label{lem:exact-penalty}
Suppose \eqref{eq:population-saddle-gap} holds for target $b$ and
$\Lambda>\lambda_b^\star$.  Then
\begin{align}
  C(\overline w_T)&\le C^\star(b)+e_T,
  \label{eq:population-cost}\\
  H(\overline w_T)&\le
  b+\frac{e_T}{\Lambda-\lambda_b^\star}.
  \label{eq:population-feasibility}
\end{align}
\end{lemma}

\begin{proof}
Let $w_b^\star$ be a primal optimum.  Since it is feasible and
$\overline\lambda_T\ge0$,
\[
  \min_u F(u,\overline\lambda_T)
  \le F(w_b^\star,\overline\lambda_T)
  \le C^\star(b).
\]
Therefore \eqref{eq:population-saddle-gap} implies
\begin{equation}
  C(\overline w_T)
  +\Lambda[H(\overline w_T)-b]_+
  \le C^\star(b)+e_T.
  \label{eq:penalized-upper}
\end{equation}
Setting the dual price to zero inside the maximum gives
\eqref{eq:population-cost}.

Strong duality at $\lambda_b^\star$ gives, for every $w$,
\[
  C(w)+\lambda_b^\star(H(w)-b)\ge C^\star(b).
\]
If $H(\overline w_T)\le b$, there is nothing to prove.  Otherwise, put
$v=H(\overline w_T)-b>0$.  Then
\[
  C(\overline w_T)+\Lambda v
  \ge C^\star(b)+(\Lambda-\lambda_b^\star)v.
\]
Combining this inequality with \eqref{eq:penalized-upper} yields
$v\le e_T/(\Lambda-\lambda_b^\star)$.
\end{proof}

\subsection{Realized loss, realized cost, and proof of the main theorem}

\begin{lemma}[Online-to-realized conversion]
\label{lem:realized}
With probability at least $1-6e^{-x}$,
\begin{align}
  \frac1T\sum_{t=1}^T H_t
  &\le H(\overline w_T)+r_T,
  \label{eq:realized-H}\\
  \frac1T\sum_{t=1}^T c_t(J_t)
  &\le C(\overline w_T)+r_T,
  \label{eq:realized-base-cost}\\
  \frac1T\sum_{t=1}^T(1-D_t)A_t
  &\le a_T.
  \label{eq:realized-audits}
\end{align}
\end{lemma}

\begin{proof}
Conditional on the past, the current data are a fresh i.i.d. draw and
$J_t\sim w_t$.  Hence
\[
  \E[H_t\mid\calF_{t-1}]=H(w_t),
  \qquad
  \E[c_t(J_t)\mid\calF_{t-1}]=C(w_t).
\]
Both realized variables lie in $[0,1]$.  Hoeffding--Azuma gives
\eqref{eq:realized-H} and \eqref{eq:realized-base-cost} with the stated
$r_T$ after a union bound.

For $B_t=(1-D_t)A_t$, predictability and conditional audit independence give
\[
  \E[B_t\mid\text{pre-audit information}]
  =(1-D_t)\gamma\le\gamma.
\]
The increments are Bernoulli and have conditional variance at most $\gamma$.
Freedman's inequality yields
\[
  \sum_{t=1}^T B_t
  \le
  \gamma T+\sqrt{2\gamma Tx}+\frac{x}{3},
\]
which is \eqref{eq:realized-audits}.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:main}]
On the population saddle event, Lemmas~\ref{lem:dual-bound} and
\ref{lem:exact-penalty}, with $b=\bar\eps$, give
\[
  C(\overline w_T)\le C^\star(\bar\eps)+e_T,
  \qquad
  H(\overline w_T)
  \le\bar\eps+\frac{e_T}{\Lambda-1/\bar\eps}.
\]
The latter uses $\lambda^\star_{\bar\eps}\le1/\bar\eps$.
Intersect this event with Lemma~\ref{lem:realized}; the definition of $x$
makes the combined failure probability at most $\delta$.
Equation \eqref{eq:realized-H} proves \eqref{eq:main-H}.
Audit-and-correct gives $G_t\le H_t$ pointwise, proving
\eqref{eq:main-G}.  Finally,
\[
  C_t^{\mathrm{tot}}
  =c_t(J_t)+(1-D_t)A_t.
\]
Combining \eqref{eq:realized-base-cost},
\eqref{eq:realized-audits}, and the population cost bound proves
\eqref{eq:main-cost}.
\end{proof}

\subsection{Tightening and proof of the exact-error corollary}

\begin{lemma}[Cost of tightening]
\label{lem:tightening}
For every $0\le\kappa\le\eps$,
\begin{equation}
  C^\star(\eps-\kappa)
  \le C^\star(\eps)+\frac{\kappa}{\eps}.
  \label{eq:value-lipschitz}
\end{equation}
\end{lemma}

\begin{proof}
Let $w^\star_\eps$ solve \eqref{eq:population-comparator}, let $e_K$ be the
always-expert policy, and set $\alpha=\kappa/\eps$.  The mixture
\[
  w'=(1-\alpha)w^\star_\eps+\alpha e_K
\]
satisfies
\[
  H(w')=(1-\alpha)H(w^\star_\eps)
  \le(1-\alpha)\eps=\eps-\kappa.
\]
Its cost obeys
\[
  C(w')
  =(1-\alpha)C^\star(\eps)+\alpha C(e_K)
  \le C^\star(\eps)+\alpha,
\]
because $C(e_K)=1$.  Optimality at level $\eps-\kappa$ proves the claim.
\end{proof}

\begin{proof}[Proof of Corollary~\ref{cor:exact}]
Since $\kappa_T\le\eps/2$, we have
$\bar\eps\ge\eps/2$.  Consequently
\[
  \Lambda-\frac1{\bar\eps}
  \ge\frac4\eps-\frac2\eps
  =\frac2\eps.
\]
Theorem~\ref{thm:main} therefore gives
\[
  \frac1T\sum_{t=1}^T H_t
  \le
  \bar\eps+\frac{\eps e_T}{2}+r_T
  =\eps,
\]
which proves \eqref{eq:exact-error}.  Lemma~\ref{lem:tightening} and
\eqref{eq:main-cost} give
\[
  \frac1T\sum_{t=1}^T C_t^{\mathrm{tot}}
  \le
  C^\star(\eps)+\frac{\kappa_T}{\eps}
  +e_T+r_T+a_T.
\]

It remains to check the rate.  With $\gamma=T^{-1/3}$,
$V_T=\widetilde O(T^{4/3})$.  Hence
$S_w=\widetilde O(\Lambda^2T^{4/3})$ and
$S_\lambda=\widetilde O(T^{4/3})$.  The learning rates in
\eqref{eq:eta-w}--\eqref{eq:eta-lambda} give
\[
  R_w+R_\lambda+R_{\mathrm{stoch}}
  =\widetilde O((1+\Lambda)T^{2/3}).
\]
Thus $e_T=\widetilde O((1+\Lambda)T^{-1/3})$ and
$a_T=O(T^{-1/3})$ up to logarithmic terms.  Substituting
$\Lambda=4/\eps$ and multiplying the average-cost bound by $T$ proves
\eqref{eq:T23-summary}.
\end{proof}

\section{Interpretation and scope}
\label{sec:scope}

\paragraph{What the theorem adds.}
The existing online theorem controls error for any data sequence but does not
compare cost with an oracle.  The present direction adds a primal policy
learner and proves a comparison with the cheapest fixed randomized threshold
policy whose population counterfactual loss is at most $\eps$.  All expert
audits are charged to the algorithm.

\paragraph{Meaning of distribution-free.}
The result is uniform over all i.i.d. distributions $P$; it assumes no
parametric model and no calibrated proxy.  It is not distribution-free in the
stronger arbitrary-sequence sense.  The i.i.d. assumption is what lets past
audits reveal the future population cost and loss of a fixed policy.

\paragraph{Why the comparator uses counterfactual loss.}
Audited AI mistakes are corrected, so their final released-label loss is zero.
Using final loss alone would make an unsafe AI source appear perfect whenever
it is audited.  The constraint therefore controls $H_t$, the loss the selected
AI action would have incurred before correction.  Since $G_t\le H_t$, this
automatically controls the released labels as well.

\paragraph{Fixed scores and policies.}
The first theorem freezes the AI model, score function, and threshold grid.
Allowing the proxy itself to be retrained from past audits is a distinct
adaptive-policy problem.  It would require either sample splitting, a
complexity-controlled adaptive class, or a sequential uniform-convergence
argument.

\paragraph{Several cheap sources.}
The proof extends algebraically to a finite class of multi-source routing
policies if an observed expert label reveals the counterfactual loss of every
candidate policy.  In practice this may require evaluating every cheap model.
Those model-call costs must then be included in $c_t(k)$.  Without such full
counterfactual observability, the feedback becomes a contextual bandit problem
and the importance weights and regret rate change.

\paragraph{Conference-paper status.}
The threshold LP, cost-sensitive routing, and inverse-probability auditing are
not individually novelty claims.  A defensible contribution would be the
simultaneous high-probability error and audit-inclusive cost guarantee, ideally
paired with a lower bound showing whether the $T^{2/3}$ gap-free rate is
optimal and experiments that report every component of total cost.

\end{document}
