\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{mathrsfs}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{float}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    citecolor=blue,
    urlcolor=blue
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.5\baselineskip}

\makeatletter
\renewcommand\section{\@startsection{section}{1}{\z@}%
  {-1.4ex plus -0.4ex minus -.2ex}%
  {0.6ex plus .2ex}%
  {\normalfont\Large\bfseries}}
\renewcommand\subsection{\@startsection{subsection}{2}{\z@}%
  {-1.1ex plus -0.3ex minus -.2ex}%
  {0.45ex plus .15ex}%
  {\normalfont\large\bfseries}}
\renewcommand\subsubsection{\@startsection{subsubsection}{3}{\z@}%
  {-0.9ex plus -0.2ex minus -.2ex}%
  {0.35ex plus .1ex}%
  {\normalfont\normalsize\bfseries}}
\makeatother

\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{assumption}{Assumption}
\newtheorem{remark}{Remark}
\newtheorem{definition}{Definition}

\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\Pp}{\mathbb{P}}
\newcommand{\ind}[1]{\mathbf{1}\{#1\}}
\newcommand{\calD}{\mathcal{D}}
\newcommand{\calA}{\mathcal{A}}
\newcommand{\calL}{\mathcal{L}}
\newcommand{\calG}{\mathcal{G}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calP}{\mathcal{P}}
\newcommand{\hatY}{\widehat Y}
\newcommand{\tildeY}{\widetilde Y}
\newcommand{\hatell}{\widehat \ell}
\newcommand{\hath}{\widehat h}
\newcommand{\hatL}{\widehat L}
\newcommand{\hatC}{\widehat C}
\newcommand{\eps}{\varepsilon}
\newcommand{\lam}{\lambda}
\newcommand{\Lam}{\Lambda}
\newcommand{\argmin}{\operatorname*{arg\,min}}
\newcommand{\argmax}{\operatorname*{arg\,max}}

\newcommand{\zwy}[1]{\textcolor{red}{\textbf{WY: #1}}}

\begin{document}
\vspace*{-0.65in}
\begin{center}
{\Large\bfseries Online PAC Labeling from a Linear Programming Perspective\par}
\vspace{0.35em}
Wanyu Zhang \quad Lutong Hao \quad Daohong Tu
\end{center}
\vspace{-0.6em}

\noindent\textbf{Abstract.}
We present PAC labeling from a finite-pool linear-programming perspective and
use this view to motivate an online audited extension.  Offline, the LP dual
induces a scalar price of error: proxy losses determine the routed cheap
source and expert deferral, while held-out labels certify the selected policy.
Online, the method maintains a moving
threshold and uses randomized expert audits to obtain inverse-probability
feedback for updating it.  Under predictable proxy scores and independent
audits, this gives finite-horizon high-probability control of the realized
error of the released labels.

\section{Problem Setup and LP Formulation}
\label{sec:optimization-dual}

\subsection{Setup and Notation}

There is a fixed pool of unlabeled items $X_1,\ldots,X_T$,
whose true labels $Y_1,\ldots,Y_T$ are initially unknown, and the goal is to labeling the items correctly while minimizing labeling cost.

Define the action set
\(
    \calA = \{E,1,\ldots,k\},
\)
where $E$ denotes deferral to the expert. The expert label $Y_t$ is treated as correct but incurs an 
expansive query cost $c_{t}(E)>0$. For each item $X_t$, we have access to $k$ cheap ML models, which produce predicted labels
\(\hatY_t^{(j)}\). 

In this project, we assume ML models are much cheaper 
than the expert. Therefore, define the loss $h_t(a)$ and 
cost $c_t(a)$ for action $a$ on item $X_t$ by
\begin{equation}
    h_t(a)
    =
    \begin{cases}
        0, & a=E,\\
        \ell\bigl(Y_t,\hatY_t^{(a)}\bigr), & a\in[k],
    \end{cases}
    \qquad
    c_t(a)
    =
    \begin{cases}
        1, & a=E,\\
        0, & a\in[k].
    \end{cases}
    \label{eq:itemwise-loss-cost}
\end{equation}
The labeling loss is assumed bounded and normalized:
\(
    0 \le \ell\bigl(Y_t,\hatY_t^{(j)}\bigr) \le 1,
    \, \forall t\in[T],\; j\in[k].
\)

% For $a\in\calA$, define the loss and cost for item $t$ by

A labeling rule chooses an action $a_t\in\calA$ for each item.
The resulting final label is
\[
    \tildeY_t
    =
    \begin{cases}
        Y_t, & a_t=E,\\
        \hatY_t^{(a_t)}, & a_t\in[k].
    \end{cases}
\]

\subsection{The Cost-Aware Labeling LP}

We formulate the cost-aware PAC labeling problem as a linear program.
Intuitively, the LP minimizes labeling cost subject to an average-error constraint. The LP explicitly takes both the cost and the loss into account, 
and it models multi-source setting.

Let $x_{t,a}$ be the probability of choosing action $a$ on item $t$.
If the true losses $h_t(a)$ were known,
the optimal labeling policy would be the solution to the following LP:
\begin{equation}
\label{eq:oracle-lp}
\begin{aligned}
    \textnormal{minimize}_{x}\quad
    \frac1T\sum_{t=1}^T\sum_{a\in\calA} c_t(a)x_{t,a}
    \qquad
    \textnormal{subject to}\quad
    & \frac1T\sum_{t=1}^T\sum_{a\in\calA} h_t(a)x_{t,a} \le \eps,
    \\
    & \sum_{a\in\calA}x_{t,a}=1,\qquad t\in[T],
    \\
    & x_{t,a}\ge0,\qquad t\in[T],\; a\in\calA.
\end{aligned}
\end{equation}


\subsection{Lagrangian Dual and Shadow Price}

The oracle LP \eqref{eq:oracle-lp} has a single global average-error constraint.
Let $\lambda\ge0$ denote the Lagrange multiplier, or shadow price, of the labeling error constraint.
The dual problem is the one-dimensional concave maximization problem (See Appendix \ref{app:dual-derivation} for details):
\begin{equation}
    \max_{\lambda\ge0}
    D(\lambda)
    :=
    -\lambda\eps
    +
    \frac1T\sum_{t=1}^T
    \min_{a\in\calA}\{c_t(a)+\lambda h_t(a)\}.
    \label{eq:dual-problem}
\end{equation}
This is the source of the fixed-price rule: once a price $\lambda$ is fixed,
the dual minimization separates across items, and the action for item $t$ is given by the following simple rule:
\begin{equation}
    a_t(\lambda)
    \in
    \argmin_{a\in\calA}
    \{c_t(a)+\lambda h_t(a)\}.
    \label{eq:true-price-action}
\end{equation}
The dual price $\lambda$ balances the trade-off between cost and error.

\subsection{Roadmap}
The LP perspective suggests a one-dimensional dual price $\lambda$ for trading
off expert cost against labeling error. Since the oracle rule depends on the
unknown losses \(h_t(a)\), the offline method below uses proxy losses
\(\hath_t(a)\) to build a family of price-indexed policies. The proxy may be
obtained from a labeled training split by regression, isotonic calibration,
multicalibration, or any other supervised procedure. The certification theorem
below does not require \(\hath\) to be conservative or well calibrated. Better
proxies reduce cost; held-out calibration supplies validity.
Throughout the offline analysis, \(\hath_t(a)\) is treated as a fixed proxy
loss for item \(X_t\) and action \(a\); it may be a deterministic function of
\(X_t\), or the output of a model trained on an independent split before the
target pool is calibrated.
For simplicity, we assume throughout that the itemwise losses used in the
argmin rules are distinct across actions; in particular, \(h_t(a)\) is different
for different \(a\), i.e., no ties occur.

In the \textbf{offline setting}, Section~\ref{sec:offline-certification} first
estimates a certified price on a calibration set and then labels the target pool
at the fixed price \(\hat\lambda\).
    
In the \textbf{online setting}, items arrive online and labels are revealed only intermittently through random audits.
Whenever the true label is observed, we obtain feedback about the realized
loss $h_t$ and update the price $\lambda_t$ through an online dual update.

\section{Offline PAC Labeling}
\label{sec:offline-certification}

In this section, the offline procedure follows the operational order of the
algorithm. First, we use a labeled calibration sample to select a certified
price \(\hat\lambda\). Then we label the full target pool using the fixed price
\(\hat\lambda\).

\subsection{Price Estimation on a Calibration Set}
\label{sec:calibration-selection}

For price estimation, we form the plug-in policy family by replacing the
unknown loss \(h_t(a)\) in \eqref{eq:true-price-action} with the fixed proxy loss
\(\hath_t(a)\).
In the equal-cost setting \(c_t(j)=0\) and \(c_t(E)=1\), the chosen cheap
source is independent of \(\lambda\): first set
\begin{equation}
    j_t^\lambda=j_t^\star
    \in \argmin_{j\in[k]}\hath_{t}(j),
    \qquad
    s_t=\hath_t(j_t^\star)=\min_{j\in[k]}\hath_t(j).
    \label{eq:proxy-j-star}
\end{equation}
The price \(\lambda\) then only decides whether to accept this routed cheap
label or defer to the expert:
\begin{equation}
    D_t^\lambda
    =
    \ind{s_t\ge 1/\lambda},
    \qquad
    a_t^\lambda
    =
    \begin{cases}
        E, & D_t^\lambda=1,\\
        j_t^\star, & D_t^\lambda=0,
    \end{cases}
    \label{eq:proxy-action}
\end{equation}
with the conventions \(1/0=\infty\) and \(1/\infty=0\).
Equivalently,
\[
    a_t^\lambda
    \in
    \argmin_{a\in\calA}
    \{c_t(a)+\lambda\hath_t(a)\}.
\]
The realized labeling loss and the cost given a price $\lambda$ are then
\begin{equation}
    H_t(\lambda)
    =
    (1-D_t^\lambda)
    \ell\bigl(Y_t,\hatY_t^{(j_t^\star)}\bigr),\qquad 
    C_t(\lambda)
    =
    D_t^\lambda.
    \label{eq:H-C-lambda}
\end{equation}

Then the average loss and cost of the price-$\lambda$ policy are
\begin{equation}
    L_T(\lambda)=\frac1T\sum_{t=1}^T H_t(\lambda),
    \qquad
    C_T(\lambda)=\frac1T\sum_{t=1}^T C_t(\lambda).
    \label{eq:L-C-lambda}
\end{equation}
Here \(C_T(\lambda)\) is known from the proxies and costs, while
\(L_T(\lambda)\) depends on true labels. The calibration set is used exactly to
estimate this loss.

We sample calibration indices \(I_1,\ldots,I_m\) independently and uniformly
from the target pool, with replacement, and collect the corresponding expert
labels. Define the empirical
labeling loss
\begin{equation}
    \hatL_m(\lambda)
    =
    \frac1m\sum_{s=1}^m H_{I_s}(\lambda).
    \label{eq:empirical-cal-loss}
\end{equation}
For any fixed \(\lambda\), Hoeffding's inequality gives a one-sided upper
confidence bound on \(L_T(\lambda)\):
\begin{equation}
    U_m(\lambda;\alpha)
    =
    \hatL_m(\lambda)
    +
    \sqrt{\frac{\log(1/\alpha)}{2m}}.
    \label{eq:hoeffding-ucb}
\end{equation}
We do not need a union bound over \(\lambda\) here: as \(\lambda\) increases,
the threshold \(1/\lambda\) decreases, so each item can only move from the
routed AI model to the expert and cannot switch between cheap models. Thus
\(H_t(\lambda)\) is non-increasing and \(C_t(\lambda)\) is non-decreasing in
\(\lambda\).
The certified price is
\begin{equation}
    \hat\lambda
    =
    \min\left\{\lambda\ge0 : U_m(\lambda;\alpha)\le\eps\right\},
    \label{eq:certified-price-selection}
\end{equation}
falling back to the expert-only policy $\lambda=\infty$ if no finite price
qualifies. Because $C_T(\lambda)$ is non-decreasing and $U_m(\lambda;\alpha)$
non-increasing in $\lambda$, \eqref{eq:certified-price-selection} coincides with
the cost-minimizing selection
$\argmin_{\lambda\in[0,\infty]}\{C_T(\lambda):U_m(\lambda;\alpha)\le\eps\}$.

\subsection{Labeling the Pool at Price \texorpdfstring{$\hat\lambda$}{lambda-hat}}
\label{sec:proxy-estimation}

After calibration, the price is fixed. The final labeling rule is the plug-in
dual rule at \(\hat\lambda\):
\[
    a_t^{\hat\lambda}
    \in
    \argmin_{a\in\calA}
    \{c_t(a)+\hat\lambda\hath_t(a)\}.
\]
In the equal-cost form this rule is especially simple. For each target item,
compute \(j_t^\star\) and \(s_t\) from \eqref{eq:proxy-j-star}. If
\(s_t\ge1/\hat\lambda\), query the expert and release \(\tildeY_t=Y_t\).
Otherwise, accept the routed cheap label and release
\(\tildeY_t=\hatY_t^{(j_t^\star)}\).

The overall offline labeling algorithm is summarized in Algorithm~\ref{alg:offline-fixed-price}.

\begin{algorithm}[ht]
\caption{Offline fixed-price labeling}
\label{alg:offline-fixed-price}
\begin{algorithmic}[1]
\Require Unlabeled pool $X_1,\ldots,X_T$; cheap predictions $\{\hatY_t^{(j)}\}_{j\in[k]}$; proxy losses $\{\hath_{t}(j)\}_{j\in[k]}$; target error $\eps$; failure level $\alpha$.
\Statex \textbf{Stage 1: Price estimation on a calibration set}
\State Sample calibration indices $I_1,\ldots,I_m\stackrel{\mathrm{i.i.d.}}{\sim}\operatorname{Unif}([T])$ and collect expert labels $\{Y_{I_s}\}_{s=1}^m$.
\State Form the empirical loss $\hatL_m(\lambda)$ \eqref{eq:empirical-cal-loss} and the level-$(1-\alpha)$ upper confidence bound $U_m(\lambda;\alpha)$ \eqref{eq:hoeffding-ucb}.
\State Select the certified price
       $\hat\lambda=\min\{\lambda\ge0 : U_m(\lambda;\alpha)\le\eps\}$ \eqref{eq:certified-price-selection}.
\Statex \textbf{Stage 2: Label the pool at price $\hat\lambda$}
\For{$t=1,\ldots,T$}
    \State Pick the best cheap model $j_t\in\argmin_{j\in[k]}\hath_{t}(j)$.
    \State \textbf{If} $\hath_{t}(j_t)\ge 1/\hat\lambda$: query expert, $\tildeY_t \gets Y_t$.
    \State \textbf{Else}: accept cheap label, $\tildeY_t \gets \hatY_t^{(j_t)}$.
\EndFor
\Ensure Labels $\tildeY_1,\ldots,\tildeY_T$ with certified error $\le\eps$ at level $1-\alpha$.
\end{algorithmic}
\end{algorithm}



\paragraph{Relation to PAC labeling}

Under the single-source case, if we use uncertainty score as the proxy, $\hath_t = U_t$, then AI label is used when
\[
    \hath_t = U_t < 1/\hat\lambda.
\]
This corresponds to the threshold policy used in the original PAC labeling method \cite{candes2025paclabels}.
Differently, the threshold used in our method is defined by the dual price motivated from the LP perspective.
With multiple sources, $\hath_t$ is replaced by the
itemwise minimum of the proxy losses.


\subsection{Offline PAC Guarantees}


\begin{theorem}[Offline monotone-threshold PAC guarantee]
\label{thm:offline-fixed-price-pac}
Let \(\hat\lambda\) be
selected over \([0,\infty]\) by \eqref{eq:certified-price-selection}. Then,
with probability at least \(1-\alpha\) over the draw of the calibration
indices, the released labels satisfy
\begin{equation}
    \frac1T\sum_{t=1}^T \ell(Y_t,\tildeY_t)\le\eps.
    \label{eq:offline-pac-guarantee}
\end{equation}
\end{theorem}

\noindent
The proof is in Appendix~\ref{app:proofs}. The same calibration idea also gives
an inductive version.

\begin{corollary}[Generalization guarantee]
\label{cor:inductive-deployment}
Suppose the calibration set is an i.i.d.\ sample from a distribution $P$. For a price
$\lambda$, define the population risk
\[
    L(\lambda)
    =
    \E_{(X,Y)\sim P}
    \left[
        (1-D^\lambda(X))
        \ell\bigl(Y,\hatY^{(j^\star(X))}(X)\bigr)
    \right].
\]
Assume the equal-cost monotone-threshold policy class above, and let
\(\hat\lambda\) be selected over \([0,\infty]\) by
\eqref{eq:certified-price-selection}.
Then $L(\hat\lambda)\le\eps$ with probability at least $1-\alpha$.
Moreover, for an independent deployment pool of size \(n\), with probability at
least \(1-\alpha-\delta\),
\begin{equation}
    \frac{1}{n}\sum_{t=1}^{n} \ell(Y_t,\tildeY_t)
    \le
    \eps + \sqrt{\frac{\log(1/\delta)}{2n}}.
    \label{eq:inductive-realized-bound}
\end{equation}
\end{corollary}

\section{Online PAC Labeling via Audits}
\label{sec:online-audited}

The offline guarantee certifies a fixed policy after a labeled calibration
stage.
In an online data-curation problem, inputs arrive sequentially, decisions are
made before future data are seen, and the loss of an AI-labeled item is
unobserved unless an expert label is revealed.
% Therefore the offline calibration argument cannot be reused directly.

The natural online analogue is to keep a moving PAC-labeling threshold. 
We propose a framework for online PAC
labeling in which randomized audits provide the intermittent feedback needed to
keep realized error controlled.

\subsection{Online PAC Labeling Setup and Audited Feedback}
\label{sec:online-free-ai}

Following the action-cost notation in \eqref{eq:itemwise-loss-cost}, we focus
on the regime
\[
    c_t(j)=0\quad\text{for all }t,j \in[k],
    \qquad
    c_t(E)=1.
\]
The online goal is therefore the same as
PAC labeling: label as many items as possible with AI while controlling the
average error of the released dataset.  The difference is that data arrive
sequentially, so the uncertainty threshold is updated over time.

At time $t$, the learner observes the input $X_t$, cheap model labels
$\{\hatY_t^{(j)}\}_{j=1}^k$, and predictable proxy losses
$\{\hath_t(j)\}_{j=1}^k$.  The proxy losses may be uncertainty scores,
calibrated error estimates, or any predictable scores built from past
expert/audit labels and current non-expert information.
% \textcolor{orange}{(LT: This is the delicate point:
% $\hath_t(j)$ may use $X_t$, cheap model outputs, past expert labels, and past
% audits, but it cannot use the current expert label $Y_t$, the current audit
% outcome $A_t$, or the current loss before the routing and audit decisions are
% made.)}
Though it cannot use the current expert label $Y_t$, the current audit
outcome $A_t$, or the current loss before the routing and audit decisions are
made.
The algorithm first routes the item to the model with the smallest proxy loss:
\begin{equation}
    j_t^\lambda 
    \in
    \argmin_{j\in[k]}\hath_t(j),
    \qquad
    \hath_t^\lambda =\hath_t(j_t^\lambda ).
    \label{eq:online-source}
\end{equation}
It then applies a scalar PAC-labeling threshold.  Let $\lambda_t\ge0$ denote
the current price of error.  Equivalently, $1/\lambda_t$ is the current
uncertainty threshold, with the convention that $1/\lambda_t=\infty$ when
$\lambda_t=0$.  The deferral decision is
\begin{equation}
    D_t
    =
    \ind{\lambda_t\hath_t^\lambda\ge1}
    =
    \ind{\hath_t^\lambda\ge 1/\lambda_t}.
    \label{eq:online-defer}
\end{equation}
If $D_t=1$, the item is sent to the expert and the released label is
$\tildeY_t=Y_t$.  If $D_t=0$, the algorithm initially releases the routed AI
label $\tildeY_t=\hatY_t^{(j_t^\lambda)}$.  This is exactly the PAC-labeling
threshold form.  The multi-model extension is contained in the
routed score $\hath_t^\lambda=\min_j\hath_t(j)$.

The main online obstacle is partial feedback.  When an AI label is used, its
true loss is unobserved unless the expert label is also revealed.  Therefore,
after every AI decision, the algorithm uses an audit probability chosen in
advance of the audit draw and before observing the current expert label:
\[
    A_t\sim\mathrm{Bernoulli}(p_t),
    \qquad p_t\in[p_{\min},1].
\]
If $A_t=1$, the expert label is queried, the final released label is
corrected to $Y_t$, and the audit records the counterfactual error of the
routed AI label.

Define the counterfactual AI-decision loss
\[
    H_t
    =
    (1-D_t)\ell\bigl(Y_t,\hatY_t^{(j_t^\lambda)}\bigr).
\]
Deferral has zero loss because the expert label is used.  An unaudited AI
decision may have nonzero loss, but that loss is not observed.  The update
uses an internal target $\eps_0\le\eps$:
\[
    \widehat Z_t
    =
    \begin{cases}
        -\eps_0,
        & \text{if the item is deferred to the expert},\\[2mm]
        \{\ell(Y_t,\hatY_t^{(j_t^\lambda)})-\eps_0\}/p_t,
        & \text{if the AI label is used and audited},\\[2mm]
        0,
        & \text{if the AI label is used and not audited}.
    \end{cases}
\]
The role of $\eps_0$ is to leave room for finite-horizon statistical guarantee:
the algorithm updates toward the internal target $\eps_0$, while the final PAC
target is $\eps$.  Corollary~\ref{cor:online-pac-tuning} gives the condition
under which choosing $\eps_0$ yields final error at most $\eps$.
The price update is
\begin{equation}
    \lambda_{t+1}=[\lambda_t+\eta\widehat Z_t]_+,
    \label{eq:online-price-update}
\end{equation}
where $\eta>0$ is a step size.
When audited AI mistakes occur more often than the internal target
\(\eps_0\), the update increases \(\lambda_t\), lowers the threshold
\(1/\lambda_t\), and makes future routing more conservative.  When
deferrals or low-error audits dominate, the price decreases and the algorithm
allows more AI labels.

Let $G_t=\ell(Y_t,\tildeY_t)$ be the realized final loss after
audit-and-correct.  Since audited AI errors are corrected (so loss becomes zero), and expert deferrals
use the true label,
\[
    G_t\le H_t.
\]
The reported final error is the realized error $G_t$ after audit-and-correct, whereas
the counterfactual AI error tracks how often the routed AI label would have
been wrong before correction.  This distinction is important: audits serve
both as intermittent feedback for the moving PAC threshold and as corrections
for the final dataset.

\begin{algorithm}[ht]
\caption{Audited online PAC labeling}
\label{alg:online-audited}
\begin{algorithmic}[1]
\Require Stream horizon $T$; target error $\eps\in[0,1]$; audit floor
$p_{\min}$; step size $\eta$; internal target
$\eps_0\in[0,\eps]$.
\State Initialize $\lambda_1\ge0$.
\For{$t=1,\ldots,T$}
    \State Observe $X_t$, cheap labels $\{\hatY_t^{(j)}\}_{j=1}^k$, and
    predictable proxies $\{\hath_t(j)\}_{j=1}^k$.
    \State Choose $j_t^\lambda$ and $\hath_t^\lambda$ by \eqref{eq:online-source}.
    \If{$\lambda_t\hath_t^\lambda\ge1$}
        \State Query the expert, output $\tildeY_t=Y_t$, set $D_t=1$ and
        $\widehat Z_t=-\eps_0$.
    \Else
        \State Output the AI label $\tildeY_t=\hatY_t^{(j_t^\lambda)}$ and set
        $D_t=0$.
        \State Choose $p_t\in[p_{\min},1]$ before observing $Y_t$, then draw
        $A_t\sim\mathrm{Bernoulli}(p_t)$.
        \If{$A_t=1$}
            \State Query the expert, correct $\tildeY_t=Y_t$, and
            set
            $\widehat Z_t=
            \{\ell(Y_t,\hatY_t^{(j_t^\lambda)})-\eps_0\}/p_t$.
        \Else
            \State Set $\widehat Z_t=0$.
        \EndIf
    \EndIf
    \State Update $\lambda_{t+1}$ by \eqref{eq:online-price-update}.
\EndFor
\end{algorithmic}
\end{algorithm}

\subsection{Online Finite-Horizon Guarantee}

The online result is distribution-free with respect to the data sequence; the
probability is over the algorithm's audit randomness.
It controls realized error, not regret against an offline expert-query oracle.

\begin{assumption}[Predictable routing and random audits]
The routing decision, audit probability, and selected source are chosen using
only past information and the current non-expert information
$(X_t,\{\hatY_t^{(j)},\hath_t(j)\}_{j=1}^k)$.
After this decision, the audit draw is independent Bernoulli with known
probability $p_t\in[p_{\min},1]$.
\end{assumption}

\begin{assumption}[Proxy floor]
For some $\rho>0$, $\hath_t(j)\in[\rho,1]$ for all $t,j$.
\end{assumption}

For the finite-horizon analysis, define the augmented observation mask and its
conditional observation probability by
\begin{equation}
    O_t=D_t+(1-D_t)A_t,
    \qquad
    q_t=D_t+(1-D_t)p_t .
    \label{eq:online-augmented-mask}
\end{equation}
Thus $q_t=1$ on expert deferrals and $q_t=p_t$ on AI decisions.  The
three-case update in Algorithm~\ref{alg:online-audited} can equivalently be
written as the centered inverse-observation signal
\begin{equation}
    \widehat Z_t
    =
    \frac{O_t}{q_t}\,(H_t-\eps_0).
    \label{eq:online-centered-signal}
\end{equation}

Let $\calG_t$ denote the pre-audit sigma-field that contains the history
through round $t-1$, the current non-expert information, the selected source
$j_t^\lambda$, the deferral decision $D_t$, the audit probability $p_t$, and the
latent selected loss.  It does not contain the current audit draw $A_t$.
The audit assumption says that, conditional on $\calG_t$, $A_t$ is an
independent Bernoulli random variable with mean $p_t$ whenever $D_t=0$.

\begin{proposition}[Unbiased intermittent update signal]
\label{prop:online-unbiased}
Under bounded loss and online predictability,
\[
    \E\left[\frac{O_t}{q_t}\,\middle|\,\calG_t\right]=1,
    \qquad
    \E[\widehat Z_t\mid\calG_t]=H_t-\eps_0.
\]
\end{proposition}

\begin{theorem}[Audited online finite-horizon control]
\label{thm:online-audited}
Assume bounded loss, online predictability and audits, and the proxy floor.
Let
\[
    \lambda_{\mathrm{def}}
    =
    \frac{1}{\rho},
    \qquad
    \Lambda_{\mathrm{on}}
    =
    \max\left\{
        \lambda_1,
        \lambda_{\mathrm{def}}+\frac{\eta(1-\eps_0)}{p_{\min}}
    \right\}.
\]
Run Algorithm~\ref{alg:online-audited} with constant step size $\eta>0$ and
internal target $\eps_0\in[0,\eps]$, where $\eps\in[0,1]$.
Then, for any fixed horizon $T$ and any $\delta\in(0,1)$, with probability at
least $1-\delta$ over the audit randomness,
\begin{equation}
    \frac1T\sum_{t=1}^T H_t
    \le
    \eps_0
    +
    \frac{\Lambda_{\mathrm{on}}}{\eta T}
    +
    \frac{1}{p_{\min}}\sqrt{\frac{2\log(1/\delta)}{T}}.
    \label{eq:online-H-bound}
\end{equation}
Consequently, if audited AI labels are corrected to expert labels in the final
dataset, then
\begin{equation}
    \frac1T\sum_{t=1}^T G_t
    \le
    \eps_0
    +
    \frac{\Lambda_{\mathrm{on}}}{\eta T}
    +
    \frac{1}{p_{\min}}\sqrt{\frac{2\log(1/\delta)}{T}}.
    \label{eq:online-G-bound}
\end{equation}
\end{theorem}

\begin{corollary}[PAC-style online tuning]
\label{cor:online-pac-tuning}
Under the conditions of Theorem~\ref{thm:online-audited}, suppose
\[
    \eps_0
    +
    \frac{\Lambda_{\mathrm{on}}}{\eta T}
    +
    \frac{1}{p_{\min}}\sqrt{\frac{2\log(1/\delta)}{T}}
    \le \eps,
\]
with $\eps_0\ge0$.
Then the audit-and-correct final labels satisfy
\[
    \frac1T\sum_{t=1}^T G_t\le\eps
\]
with probability at least $1-\delta$.
With $\eta\asymp T^{-1/2}$ and constant $p_{\min}$, the slack is
$O(T^{-1/2})$.
\end{corollary}

The proofs of Proposition~\ref{prop:online-unbiased},
Theorem~\ref{thm:online-audited}, and
Corollary~\ref{cor:online-pac-tuning} are in
Appendix~\ref{app:online-proofs}.

\subsection{Offline versus Online Certification}

The online theorem is deliberately different from the offline one.
Offline calibration certifies a fixed candidate policy by evaluating it on a
held-out labeled sample.
Online auditing controls the long-run error of a moving policy by converting
unobserved AI losses into an unbiased intermittent-feedback signal.
The proxy losses again affect efficiency rather than validity, but in the
online setting some audit or reveal mechanism is essential: without it, two
streams can induce identical observations while having opposite AI-label
correctness on every unaudited item.

\section{Experiments}
\label{sec:experiments}

We run a small proof-of-concept study on ImageNet and ImageNetV2 using the
confidence score already included in the data (the datasets provided for the
last question of HW4).
There is one cheap source, namely the model prediction, and one expert source,
namely the ground-truth label. All reported numbers average over 500 random
trials. Appendix~\ref{app:experiments} gives the implementation details and full
sweeps, while Table~\ref{tab:experiment-main-results} gives representative
results at \(\eps=0.10\). The experiments are meant to check three basic points.

\begin{enumerate}[leftmargin=*]
    \item \textbf{One source.} With a single cheap source, the LP fixed-price
    rule reduces to the same scalar threshold family as the original PAC
    labeling method. We therefore recover the original PAC behavior: at
    \(\eps=0.10\), both methods have zero violations, and the expert-budget
    savings are nearly identical on ImageNet and ImageNetV2
    (Table~\ref{tab:offline-full-results}).

    \item \textbf{Two sources.} We then add a second cheap source to create a
    simple routing problem. The LP rule can choose the lower-proxy source on
    each item before deciding whether to defer to the expert. At \(\eps=0.10\),
    it still has zero violations and saves more budget than the best calibrated
    single-source baseline: \(0.7848\) versus \(0.4746\) on ImageNet, and
    \(0.5457\) versus \(0.3587\) on ImageNetV2
    (Table~\ref{tab:two-source-full-results}).

    \item \textbf{Online.} Finally, the audited online update also shows the
    desired validity--cost tradeoff. For example, at \(\eps=0.10\) and audit
    probability \(p=0.2\), both datasets have zero violations while saving
    \(0.6115\) of the expert budget on ImageNet and \(0.4681\) on ImageNetV2
    (Table~\ref{tab:online-full-results}).
\end{enumerate}

\begin{table}[htbp]
\centering
\small
\begin{tabular}{lllccc}
\toprule
Setting & Dataset & Method & Error & Violation & Budget saved \\
\midrule
One source & ImageNet & LP fixed price & 0.0873 & 0.0000 & 0.7848 \\
One source & ImageNet & Original PAC & 0.0879 & 0.0000 & 0.7864 \\
One source & ImageNetV2 & LP fixed price & 0.0718 & 0.0000 & 0.5457 \\
One source & ImageNetV2 & Original PAC & 0.0726 & 0.0000 & 0.5479 \\
\cmidrule(lr){1-6}
Two sources & ImageNet & LP routing & 0.0873 & 0.0000 & \textbf{0.7848} \\
Two sources & ImageNet & Best single source & 0.0879 & 0.0000 & 0.4746 \\
Two sources & ImageNetV2 & LP routing & 0.0718 & 0.0000 & \textbf{0.5457} \\
Two sources & ImageNetV2 & Best single source & 0.0720 & 0.0000 & 0.3587 \\
\cmidrule(lr){1-6}
Online & ImageNet & Audited, \(p=0.2\) & 0.0737 & 0.0000 & 0.6115 \\
Online & ImageNetV2 & Audited, \(p=0.2\) & 0.0783 & 0.0000 & 0.4681 \\
\bottomrule
\end{tabular}
\caption{Representative results at \(\eps=0.10\). Full sweeps and
implementation details are deferred to Appendix~\ref{app:experiments}.}
\label{tab:experiment-main-results}
\end{table}

\section{Discussion}

The report separates two regimes.
The offline method has a clean division of labor.
The proxy model and the LP structure make the policy cost efficient; the
calibration set makes it valid.
When instantiating the method, the main modeling choice is whether the target
is transductive or inductive.
If the application is dataset curation for a fixed unlabeled pool, the
transductive theorem should be the main result.
If the application is repeated deployment on future items, the inductive
statement should be foregrounded.
The online method addresses a different obstacle: the selected policy changes
over time and AI losses are not observed without expert reveal.
Random audits supply the missing feedback through an inverse-probability loss
estimate.
This gives finite-horizon error control, but not a cost-regret comparison to
the offline oracle LP.
The experiments in Section~\ref{sec:experiments} illustrate this distinction:
offline calibration gives a clean held-out certificate, while the online
mechanism exposes an explicit audit-cost versus correction tradeoff.
The main empirical limitation is that the current data contain only one cheap
source.
A stronger test of the LP perspective would use several cheap sources with
heterogeneous costs, where the original scalar threshold structure no longer
captures the routing problem.

\clearpage
\appendix

\section{Related Work}
\label{app:related-work}

\paragraph{PAC labels and conformal calibration.}
The closest starting point is PAC labeling
\cite{candes2025paclabels}, which gives finite-sample guarantees for
cost-effective dataset labeling using AI predictions and expert audits.
That framework already includes both scalar-threshold PAC labeling and
multi-model PAC routing variants.
Our formulation is best viewed as a complementary optimization-first
presentation: we start from a finite-pool cost-minimization LP, derive the
fixed-price routing rule from its dual, allow item- and source-specific costs,
and then use calibration only to certify the actual loss of the selected
proxy-generated policy.
The calibration logic is closely related to conformal prediction and
distribution-free uncertainty quantification
\cite{vovk2005,angelopoulos2021gentle}, but the object being controlled here is
the average error of a released labeled dataset rather than coverage of
prediction sets.

\paragraph{Online conformal prediction with partial feedback.}
Adaptive and online conformal methods update calibration parameters over time
to handle changing environments \cite{gibbs2021adaptive}.
Recent work has studied intermittent or semi-bandit feedback, where labels are
not always observed \cite{ge2024stochastic,wang2025mirror,yang2026adversarial}.
Those papers motivate the audited online extension in
Section~\ref{sec:online-audited}: when labels are not always revealed, the
feedback used to update a calibration or price parameter must be corrected for
the observation process.

\paragraph{Learning to defer and cost-sensitive routing.}
Learning-to-defer methods train systems that either predict or pass an item to
an expert \cite{madras2018predict,mozannar2020consistent}.
Multiple-expert and cost-sensitive variants study richer deferral and routing
settings \cite{mao2023twostage,alves2024cost}.
The distinction here is the finite-sample PAC certificate for the final
released labels.
The proxy router may be learned by standard supervised methods, but the
guarantee comes from held-out calibration of the actual selected policy.

\section{Proofs}
\label{app:proofs}

\subsection{Dual Derivation}
\label{app:dual-derivation}

Introduce one dual variable $\lambda\ge0$ for the average-error constraint and
one free dual variable $\mu_t\in\R$ for each simplex equality.
The nonnegativity constraints $x_{t,a}\ge0$ are kept as the domain of the inner
minimization.
\begin{center}
\begin{tabular}{lll}
\toprule
Primal constraint & Dual variable & Sign restriction \\
\midrule
$\frac1T\sum_{t,a} h_t(a)x_{t,a}\le\eps$
    & $\lambda$ & $\lambda\ge0$ \\
$\sum_a x_{t,a}=1$ for item $t$
    & $\mu_t$ & $\mu_t\in\R$ \\
$x_{t,a}\ge0$
    & domain constraint & -- \\
\bottomrule
\end{tabular}
\end{center}
Using the equality convention $\mu_t(1-\sum_a x_{t,a})$, the Lagrangian is
\begin{align}
    \calL(x;\lambda,\mu)
    =
    &\frac1T\sum_{t,a} c_t(a)x_{t,a}
    +\lambda\left(
        \frac1T\sum_{t,a}h_t(a)x_{t,a}-\eps
    \right)
    +\sum_{t=1}^T\mu_t\left(1-\sum_a x_{t,a}\right) \nonumber\\
    =
    &\sum_{t,a}
    \left[
        \frac1T\{c_t(a)+\lambda h_t(a)\}-\mu_t
    \right]x_{t,a}
    +\sum_{t=1}^T\mu_t-\lambda\eps .
    \label{eq:full-lagrangian}
\end{align}
For fixed $(\lambda,\mu)$, the inner problem is
$\inf_{x\ge0}\calL(x;\lambda,\mu)$.
Since the Lagrangian is linear in every $x_{t,a}$, this infimum is finite if
and only if
\begin{equation}
    \mu_t
    \le
    \frac1T\{c_t(a)+\lambda h_t(a)\},
    \qquad t\in[T],\; a\in\calA .
    \label{eq:dual-feasibility-mu}
\end{equation}
Otherwise some variable with a negative coefficient can be sent to $+\infty$,
driving the Lagrangian to $-\infty$.
When \eqref{eq:dual-feasibility-mu} holds, the $x$ terms vanish at the inner
minimum and the dual function is
\[
    g(\lambda,\mu)=\sum_{t=1}^T\mu_t-\lambda\eps .
\]
Thus the explicit dual LP is
\begin{align}
    \textnormal{maximize}_{\lambda,\mu}\quad
    & \sum_{t=1}^T\mu_t-\lambda\eps
    \label{eq:explicit-mu-dual}\\
    \textnormal{subject to}\quad
    & \mu_t
    \le
    \frac1T\{c_t(a)+\lambda h_t(a)\},
    \qquad t\in[T],\; a\in\calA, \nonumber\\
    & \lambda\ge0,\qquad \mu_t\in\R,\; t\in[T]. \nonumber
\end{align}
For any fixed $\lambda$, the objective is increasing in each $\mu_t$, so the
optimal value is attained at
\[
    \mu_t^\star(\lambda)
    =
    \frac1T\min_{a\in\calA}\{c_t(a)+\lambda h_t(a)\}.
\]
Substitution gives the reduced dual \eqref{eq:dual-problem}.
The primal is feasible because choosing the expert for all items gives zero
loss, and it is bounded because costs are nonnegative and finite.
Therefore strong duality holds by finite-dimensional linear programming
duality.

\paragraph{Proof of Theorem~\ref{thm:offline-fixed-price-pac}.}
Condition on the fixed target pool, labels, and proxy losses from the theorem.
The routed source \(j_t^\star\in\argmin_j\hath_t(j)\), the routed score
\(s_t=\hath_t(j_t^\star)\), and the routed loss
\[
    r_t=\ell(Y_t,\hatY_t^{(j_t^\star)})\in[0,1]
\]
are fixed. Under equal cheap-source costs the routed source does not depend on
\(\lambda\); the price enters only through
\[
    D_t^\lambda=\ind{s_t\ge1/\lambda},
    \qquad
    H_t(\lambda)=r_t\,\ind{s_t<1/\lambda}.
\]
Thus as \(\lambda\) increases, each item can only move from routed to deferred,
so \(H_t(\lambda)\), \(L_T(\lambda)\), and \(\hatL_m(\lambda)\) are
non-increasing in \(\lambda\).

For each fixed \(\lambda\), the calibration draws \(H_{I_s}(\lambda)\) are
i.i.d.\ in \([0,1]\) with mean \(L_T(\lambda)\). Hoeffding's inequality gives
\[
    \Pp\bigl\{L_T(\lambda)>U_m(\lambda;\alpha)\bigr\}\le\alpha,
    \qquad
    U_m(\lambda;\alpha)=\hatL_m(\lambda)+\sqrt{\tfrac{\log(1/\alpha)}{2m}}.
\]
This is a pointwise Hoeffding statement; the next monotonicity step is what removes
the need for a union bound over prices.

The equal-cost policies form a nested finite family on the fixed target pool:
as \(\lambda\) varies over \([0,\infty]\), the routed set
\(\{t:s_t<1/\lambda\}\) changes only when the threshold \(1/\lambda\) crosses one
of the finitely many scores \(s_t\). Order the distinct induced policies by
increasing \(\lambda\). If every induced policy has \(L_T(\lambda)\le\eps\), the
claim is immediate. Otherwise, let \(\lambda^\circ\) be any price inducing the
last policy in this order whose true loss is still above \(\eps\):
\[
    L_T(\lambda^\circ)>\eps,
    \qquad
    L_T(\lambda)\le\eps
    \quad\text{for every later policy.}
\]
This \(\lambda^\circ\) is fixed conditional on the target pool and labels, not
chosen from the calibration sample. If the selected price were bad, i.e.
\(L_T(\hat\lambda)>\eps\), then \(\hat\lambda\) would induce a policy no later
than \(\lambda^\circ\). Since \(U_m(\lambda;\alpha)\) is non-increasing in
\(\lambda\),
\[
    U_m(\lambda^\circ;\alpha)
    \le
    U_m(\hat\lambda;\alpha)
    \le
    \eps
    <
    L_T(\lambda^\circ).
\]
Thus the bad-selection event is contained in the single fixed-price failure
event \(\{L_T(\lambda^\circ)>U_m(\lambda^\circ;\alpha)\}\), which has
probability at most \(\alpha\). Therefore
\(\Pp\{L_T(\hat\lambda)\le\eps\}\ge1-\alpha\).

Finally, the released label equals \(\hatY_t^{(j_t^\star)}\) on routed items
and \(Y_t\) on deferred items, so
\(\frac1T\sum_t\ell(Y_t,\tildeY_t)=L_T(\hat\lambda)\). If calibration items are
corrected to their expert labels, the realized loss only decreases. \hfill$\square$

\paragraph{Proof of Corollary~\ref{cor:inductive-deployment}.}
Under equal cheap-source costs the routed source \(j^\star(X)\) does not depend
on \(\lambda\), and
\[
    H_\lambda(X,Y)
    =
    (1-D^\lambda(X))\ell(Y,\hatY^{(j^\star(X))}(X))
\]
is pointwise non-increasing in \(\lambda\). Hence \(L(\lambda)=\E H_\lambda\)
and \(\hatL_m(\lambda)\) are non-increasing. For each fixed \(\lambda\), the
calibration losses are i.i.d.\ in \([0,1]\) with mean \(L(\lambda)\), so
Hoeffding's fixed-price bound applies.

Let \(\lambda_\star=\sup\{\lambda:L(\lambda)>\eps\}\), with the claim immediate
if this set is empty. If \(L(\lambda_\star)>\eps\), the same single-point
argument as in Theorem~\ref{thm:offline-fixed-price-pac} applies at
\(\lambda_\star\). If \(L(\lambda_\star)\le\eps\), choose a deterministic
increasing sequence \(\lambda_n\uparrow\lambda_\star\) with
\(L(\lambda_n)>\eps\). On the bad event \(L(\hat\lambda)>\eps\), some
\(\lambda_n\) satisfies \(\lambda_n\ge\hat\lambda\), and therefore
\[
    U_m(\lambda_n;\alpha)
    \le U_m(\hat\lambda;\alpha)
    \le \eps
    <
    L(\lambda_n).
\]
The events \(\{U_m(\lambda_n;\alpha)\le\eps\}\) are increasing in \(n\), and for
each fixed \(n\) Hoeffding gives
\[
    \Pp\{U_m(\lambda_n;\alpha)\le\eps\}
    \le
    \Pp\{U_m(\lambda_n;\alpha)<L(\lambda_n)\}
    \le \alpha .
\]
Taking the limit over \(n\) gives \(L(\hat\lambda)\le\eps\) with probability at
least \(1-\alpha\).

Condition on the calibration sample and on the event \(L(\hat\lambda)\le\eps\).
The deployment losses \(\ell(Y_t,\tildeY_t)\) are then independent, bounded in
\([0,1]\), and have conditional mean at most \(L(\hat\lambda)\le\eps\), so
Hoeffding's inequality gives
\[
    \frac1n\sum_{t=1}^n\ell(Y_t,\tildeY_t)
    \le
    \eps+\sqrt{\frac{\log(1/\delta)}{2n}}
\]
with conditional probability at least $1-\delta$. Combining the calibration and
deployment events gives probability at least $1-\alpha-\delta$. \hfill$\square$

\subsection{Online Proofs}
\label{app:online-proofs}

\paragraph{Proof of Proposition~\ref{prop:online-unbiased}.}
Recall that $\calG_t$ fixes the predictable round-$t$ information, the selected
source $j_t^\lambda$, the routed proxy loss
$\hath_t^\lambda=\hath_t(j_t^\lambda)$, the audit probability $p_t$, the deferral
decision $D_t$, and the latent selected loss, but not the audit draw $A_t$.
If $D_t=1$, then $O_t=q_t=1$ and $H_t=0$, so
\[
    \E\left[\frac{O_t}{q_t}\,\middle|\,\calG_t\right]=1,
    \qquad
    \E[\widehat Z_t\mid\calG_t]=-\eps_0=H_t-\eps_0.
\]
If $D_t=0$, then $O_t=A_t$, $q_t=p_t$, and conditional on $\calG_t$ the audit
draw is Bernoulli$(p_t)$ while the loss
$\ell(Y_t,\hatY_t^{(j_t^\lambda)})$ is fixed.  Hence
\[
    \E\left[
        \frac{O_t}{q_t}
        \,\middle|\,
        \calG_t
    \right]
    =
    \frac{p_t}{p_t}
    =
    1.
\]
Since $H_t$ and $\eps_0$ are fixed conditional on $\calG_t$, this also gives
\[
    \E[\widehat Z_t\mid\calG_t]
    =
    \E\left[
        \frac{O_t}{q_t}(H_t-\eps_0)
        \,\middle|\,
        \calG_t
    \right]
    =
    H_t-\eps_0.
\] \hfill$\square$

\paragraph{Proof of Theorem~\ref{thm:online-audited}.}
First bound the price process.
If $\lambda_t\ge\lambda_{\mathrm{def}}=1/\rho$, then
\[
    \lambda_t\hath_t^\lambda
    =
    \lambda_t\hath_t(j_t^\lambda )
    \ge
    \lambda_{\mathrm{def}}\rho
    =
    1.
\]
Thus the algorithm defers to the expert, so $D_t=1$ and
$\widehat Z_t=-\eps_0$.
Consequently $\lambda_{t+1}=[\lambda_t-\eta\eps_0]_+\le\lambda_t$.
If instead $\lambda_t<\lambda_{\mathrm{def}}$, then
$\widehat Z_t\le(1-\eps_0)/p_{\min}$ because
$\eps_0\in[0,1]$ and the loss is bounded by one. Hence
\[
    \lambda_{t+1}
    \le
    \lambda_t+\eta(1-\eps_0)/p_{\min}
    <
    \lambda_{\mathrm{def}}+\eta(1-\eps_0)/p_{\min}.
\]
By induction, $0\le\lambda_t\le\Lambda_{\mathrm{on}}$ for all $t$.

Since $[x]_+\ge x$, the update gives
\[
    \lambda_{t+1}
    \ge
    \lambda_t+\eta\widehat Z_t.
\]
Summing over $t=1,\ldots,T$ yields
\[
    \sum_{t=1}^T \widehat Z_t
    \le
    \frac{\lambda_{T+1}-\lambda_1}{\eta}
    \le
    \frac{\Lambda_{\mathrm{on}}}{\eta}.
\]

Let $M_t=(H_t-\eps_0)-\widehat Z_t$.
By Proposition~\ref{prop:online-unbiased} and iterated expectation, $M_t$ is a
martingale difference with respect to the filtration generated by the past
rounds and the current audit draw. Moreover, $|M_t|\le1/p_{\min}$: if
$D_t=1$, then $M_t=0$; if $D_t=0$ and $A_t=0$, then
$|M_t|=|H_t-\eps_0|\le1$; and if $D_t=0$ and $A_t=1$, then
\[
    |M_t|
    =
    |H_t-\eps_0|\left|\frac{1}{p_t}-1\right|
    \le
    \frac{1}{p_t}
    \le
    \frac{1}{p_{\min}}.
\]
Azuma-Hoeffding gives, with probability at least $1-\delta$,
\[
    \sum_{t=1}^T M_t
    \le
    \frac{1}{p_{\min}}\sqrt{2T\log(1/\delta)}.
\]
Because
\[
    \sum_{t=1}^T H_t
    =
    T\eps_0+\sum_{t=1}^T\widehat Z_t+\sum_{t=1}^T M_t,
\]
combining the last displays gives \eqref{eq:online-H-bound}.
Finally, audit-and-correct gives $G_t\le H_t$ pointwise, which proves
\eqref{eq:online-G-bound}. \hfill$\square$

\paragraph{Proof of Corollary~\ref{cor:online-pac-tuning}.}
The stated condition makes the right-hand side of
\eqref{eq:online-G-bound} at most $\eps$.
If $\eta\asymp T^{-1/2}$, $p_{\min}$ is constant, and the proxy floor is fixed
so that $\Lambda_{\mathrm{on}}=O(1)$, then both excess terms in
\eqref{eq:online-G-bound} are $O(T^{-1/2})$. \hfill$\square$

\section{Experimental Details}
\label{app:experiments}

The experiments use the two ImageNet CSV files from the HW4 copy directory:
ImageNet has $T=50000$ items and ImageNetV2 has $T=10000$ items.
Each file contains a ground-truth label, a model prediction, and a confidence
score.
We treat the model prediction as the only cheap source and the ground-truth
label as the expert.
The proxy loss is $\hath=1-\textnormal{confidence}$, the cheap-source
deployment cost is zero, and the expert cost is one.
All experiments use 500 random trials.
The scripts are
\texttt{run\_simple\_offline\_\allowbreak pac\_experiment.py},
\texttt{run\_simple\_online\_\allowbreak pac\_experiment.py}, and
\texttt{run\_two\_source\_offline\_\allowbreak pac\_experiment.py}.

\paragraph{Offline implementation.}
For the fixed-price method, the candidate threshold grid contains the
expert-only rule plus 201 evenly spaced confidence-loss thresholds between
0 and 1.
This grid is an implementation choice for the sweep; the monotone certificate
in Section~\ref{sec:calibration-selection} does not require prices to be
restricted to a finite grid. The experiment uses the monotone threshold radius
\[
    \sqrt{\frac{\log(1/\alpha)}{2m}},
\]
which is valid for the selected scalar threshold by the nested-class argument
used in Theorem~\ref{thm:offline-fixed-price-pac}.
For each trial, the calibration indices are sampled independently and
uniformly from the target pool with replacement, with calibration size
$m=0.2T$.
The confidence level is $\alpha=0.05$ and
$\eps\in\{0.05,0.10,0.15\}$.
The original PAC baseline uses the same calibration sample and the same
monotone radius, but chooses its threshold directly from the calibration
mistake order instead of from the fixed grid. The full sweep over
$\eps\in\{0.05,0.10,0.15\}$ is reported in
Table~\ref{tab:offline-full-results}.

\begin{table}[htbp]
\centering
\small
\begin{tabular}{llcccc}
\toprule
Dataset & Method & $\eps$ & Error & Violation & Budget saved \\
\midrule
ImageNet   & fixed-price monotone UCB & 0.05 & 0.0372 & 0.0000 & 0.6296 \\
ImageNet   & original PAC             & 0.05 & 0.0377 & 0.0000 & 0.6323 \\
\cmidrule(lr){1-6}
ImageNet   & fixed-price monotone UCB & 0.10 & 0.0873 & 0.0000 & 0.7848 \\
ImageNet   & original PAC             & 0.10 & 0.0879 & 0.0000 & 0.7864 \\
\cmidrule(lr){1-6}
ImageNet   & fixed-price monotone UCB & 0.15 & 0.1372 & 0.0000 & 0.8851 \\
ImageNet   & original PAC             & 0.15 & 0.1380 & 0.0000 & 0.8866 \\
\cmidrule(lr){1-6}
ImageNetV2 & fixed-price monotone UCB & 0.05 & 0.0218 & 0.0000 & 0.3642 \\
ImageNetV2 & original PAC             & 0.05 & 0.0228 & 0.0000 & 0.3706 \\
\cmidrule(lr){1-6}
ImageNetV2 & fixed-price monotone UCB & 0.10 & 0.0718 & 0.0000 & 0.5457 \\
ImageNetV2 & original PAC             & 0.10 & 0.0726 & 0.0000 & 0.5479 \\
\cmidrule(lr){1-6}
ImageNetV2 & fixed-price monotone UCB & 0.15 & 0.1219 & 0.0000 & 0.6648 \\
ImageNetV2 & original PAC             & 0.15 & 0.1228 & 0.0000 & 0.6665 \\
\bottomrule
\end{tabular}
\caption{Full offline sweep. Error, violation, and budget saved are averages
over 500 trials. Rows are grouped by (dataset, $\eps$) scenario and separated
by light rules.}
\label{tab:offline-full-results}
\end{table}

\paragraph{Two-source implementation.}
\texttt{run\_two\_source\_offline\_pac\_experiment.py} constructs two
complementary cheap sources from each base ImageNet table. Items are partitioned
by the parity of the true class label. On items inside its specialty, a source
reuses the original predictor's label and confidence; outside its specialty, it
emits a random label with low confidence. The construction is seeded separately
from the trial sampler so the synthesized pool is fixed across trials; defaults
are \texttt{--synth-seed 20260526} and \texttt{--low-conf-max 0.2}. The
calibration grid contains the expert-only policy plus 201 evenly spaced
thresholds on $\min_j\hath_{t}(j)$, the calibration size is $m=0.2T$, and
$\alpha=0.05$. The LP method uses the monotone radius
$\sqrt{\log(1/\alpha)/(2m)}$; the
Bonferroni-corrected best-of-singles baseline runs both single-source
baselines at $\alpha/2$ each and reports the one with larger empirical
savings on the calibration sample. Constructed-pool statistics are written
to \texttt{results/two\_source\_offline\_pac/two\_source\_offline\_pac\_construction.csv}.
The full sweep over $\eps\in\{0.05,0.10,0.15\}$ for all four methods is in
Table~\ref{tab:two-source-full-results}.

\begin{table}[htbp]
\centering
\small
\begin{tabular}{llcccc}
\toprule
Dataset & Method & $\eps$ & Error & Violation & Budget saved \\
\midrule
ImageNet   & LP two-source monotone UCB   & 0.05 & 0.0372 & 0.0000 & \textbf{0.6296} \\
ImageNet   & Best-of-singles (Bonferroni) & 0.05 & 0.0372 & 0.0000 & 0.3782 \\
ImageNet   & Source A monotone PAC        & 0.05 & 0.0378 & 0.0000 & 0.3743 \\
ImageNet   & Source B monotone PAC        & 0.05 & 0.0378 & 0.0000 & 0.3809 \\
\cmidrule(lr){1-6}
ImageNet   & LP two-source monotone UCB   & 0.10 & 0.0873 & 0.0000 & \textbf{0.7848} \\
ImageNet   & Best-of-singles (Bonferroni) & 0.10 & 0.0879 & 0.0000 & 0.4746 \\
ImageNet   & Source A monotone PAC        & 0.10 & 0.0878 & 0.0000 & 0.4715 \\
ImageNet   & Source B monotone PAC        & 0.10 & 0.0877 & 0.0000 & 0.4754 \\
\cmidrule(lr){1-6}
ImageNet   & LP two-source monotone UCB   & 0.15 & 0.1372 & 0.0000 & \textbf{0.8851} \\
ImageNet   & Best-of-singles (Bonferroni) & 0.15 & 0.1383 & 0.0000 & 0.5296 \\
ImageNet   & Source A monotone PAC        & 0.15 & 0.1377 & 0.0000 & 0.5273 \\
ImageNet   & Source B monotone PAC        & 0.15 & 0.1379 & 0.0000 & 0.5299 \\
\cmidrule(lr){1-6}
ImageNetV2 & LP two-source monotone UCB   & 0.05 & 0.0218 & 0.0000 & \textbf{0.3642} \\
ImageNetV2 & Best-of-singles (Bonferroni) & 0.05 & 0.0210 & 0.0000 & 0.2331 \\
ImageNetV2 & Source A monotone PAC        & 0.05 & 0.0227 & 0.0000 & 0.2254 \\
ImageNetV2 & Source B monotone PAC        & 0.05 & 0.0230 & 0.0000 & 0.2424 \\
\cmidrule(lr){1-6}
ImageNetV2 & LP two-source monotone UCB   & 0.10 & 0.0718 & 0.0000 & \textbf{0.5457} \\
ImageNetV2 & Best-of-singles (Bonferroni) & 0.10 & 0.0720 & 0.0000 & 0.3587 \\
ImageNetV2 & Source A monotone PAC        & 0.10 & 0.0727 & 0.0000 & 0.3470 \\
ImageNetV2 & Source B monotone PAC        & 0.10 & 0.0730 & 0.0000 & 0.3629 \\
\cmidrule(lr){1-6}
ImageNetV2 & LP two-source monotone UCB   & 0.15 & 0.1219 & 0.0000 & \textbf{0.6648} \\
ImageNetV2 & Best-of-singles (Bonferroni) & 0.15 & 0.1226 & 0.0000 & 0.4389 \\
ImageNetV2 & Source A monotone PAC        & 0.15 & 0.1234 & 0.0000 & 0.4287 \\
ImageNetV2 & Source B monotone PAC        & 0.15 & 0.1226 & 0.0000 & 0.4412 \\
\bottomrule
\end{tabular}
\caption{Full two-source sweep. Error, violation, and budget saved are
averages over 500 trials of calibration sampling. Rows are grouped by
(dataset, $\eps$) scenario and separated by light rules; the largest budget
saved in each scenario is shown in bold.}
\label{tab:two-source-full-results}
\end{table}

\paragraph{Online implementation.}
For each trial, the target pool is randomly permuted into a stream.
The update uses $\eta=1$, proxy floor $\rho=0.01$, and
$\lambda_1=1/\eps$.
The online routing rule uses the AI prediction when
$\lambda_t\max(1-\textnormal{confidence}_t,\rho)<1$ and otherwise defers to
the expert.
If the AI prediction is used, it is audited with probability
$p\in\{0.1,0.2,0.5\}$.
The hybrid intermittent update is $-\eta\eps_0$ on expert deferrals,
$\eta(\ell_t-\eps_0)/p$ on audited AI decisions, and zero on unaudited AI
decisions.
Audited AI labels are corrected by the expert before release; unaudited AI
labels are released as-is.
The reported ``AI error'' is the counterfactual average loss before audit
correction, and the reported final error is the realized loss after
correction.
As noted in Section~\ref{sec:experiments}, these runs set $\eps_0=\eps$
rather than subtracting the finite-horizon slack from
Corollary~\ref{cor:online-pac-tuning}. The full sweep over
$\eps\in\{0.05,0.10,0.15\}$ and $p\in\{0.1,0.2,0.5\}$ is reported in
Table~\ref{tab:online-full-results}.

\begin{table}[htbp]
\centering
\small
\begin{tabular}{lcccccc}
\toprule
Dataset & $\eps$ & $p$ & Final error & AI error & Violation & Budget saved \\
\midrule
ImageNet   & 0.05 & 0.1 & 0.0436 & 0.0485 & 0.0100 & 0.5738 \\
ImageNet   & 0.05 & 0.2 & 0.0394 & 0.0493 & 0.0000 & 0.5244 \\
ImageNet   & 0.05 & 0.5 & 0.0249 & 0.0497 & 0.0000 & 0.3344 \\
\cmidrule(lr){1-7}
ImageNet   & 0.10 & 0.1 & 0.0780 & 0.0866 & 0.0000 & 0.6629 \\
ImageNet   & 0.10 & 0.2 & 0.0737 & 0.0921 & 0.0000 & 0.6115 \\
ImageNet   & 0.10 & 0.5 & 0.0490 & 0.0981 & 0.0000 & 0.3952 \\
\cmidrule(lr){1-7}
ImageNet   & 0.15 & 0.1 & 0.1017 & 0.1130 & 0.0000 & 0.7159 \\
ImageNet   & 0.15 & 0.2 & 0.0979 & 0.1223 & 0.0000 & 0.6626 \\
ImageNet   & 0.15 & 0.5 & 0.0683 & 0.1367 & 0.0000 & 0.4330 \\
\cmidrule(lr){1-7}
ImageNetV2 & 0.05 & 0.1 & 0.0445 & 0.0494 & 0.1840 & 0.4140 \\
ImageNetV2 & 0.05 & 0.2 & 0.0393 & 0.0491 & 0.0100 & 0.3750 \\
ImageNetV2 & 0.05 & 0.5 & 0.0244 & 0.0489 & 0.0000 & 0.2372 \\
\cmidrule(lr){1-7}
ImageNetV2 & 0.10 & 0.1 & 0.0863 & 0.0958 & 0.0400 & 0.5091 \\
ImageNetV2 & 0.10 & 0.2 & 0.0783 & 0.0979 & 0.0000 & 0.4681 \\
ImageNetV2 & 0.10 & 0.5 & 0.0499 & 0.0996 & 0.0000 & 0.3010 \\
\cmidrule(lr){1-7}
ImageNetV2 & 0.15 & 0.1 & 0.1197 & 0.1331 & 0.0000 & 0.5731 \\
ImageNetV2 & 0.15 & 0.2 & 0.1126 & 0.1407 & 0.0000 & 0.5330 \\
ImageNetV2 & 0.15 & 0.5 & 0.0739 & 0.1479 & 0.0000 & 0.3465 \\
\bottomrule
\end{tabular}
\caption{Full online sweep. Final error, AI error, and budget saved are
averages over 500 trials. Rows are grouped by (dataset, $\eps$) scenario and
separated by light rules.}
\label{tab:online-full-results}
\end{table}

\section{Alternative Confidence Bounds}

The Hoeffding bound \eqref{eq:hoeffding-ucb} is simple but may be conservative.
Any valid one-sided mean upper confidence bound can be substituted.
For example, for a fixed $\lambda$, an empirical Bernstein bound gives
\begin{equation}
    U_m^{\mathrm{EB}}(\lambda;\alpha)
    =
    \hatL_m(\lambda)
    +
    \sqrt{\frac{2\hat V_m(\lambda)\log(2/\alpha)}{m}}
    +
    \frac{7\log(2/\alpha)}{3(m-1)},
\end{equation}
where $\hat V_m(\lambda)$ is the sample variance of $H_{I_s}(\lambda)$.

When the monotone no-grid argument does not apply, the candidate
prices can instead be certified simultaneously by a union bound. Over a finite
grid $\Lambda$, the uniform Hoeffding bound
\begin{equation}
    U_m^{\mathrm{unif}}(\lambda;\alpha)
    =
    \hatL_m(\lambda)
    +
    \sqrt{\frac{\log(|\Lambda|/\alpha)}{2m}}
    \label{eq:hoeffding-ucb-uniform}
\end{equation}
satisfies
$\Pp\{\exists\,\lambda\in\Lambda: L_T(\lambda)>U_m^{\mathrm{unif}}(\lambda;\alpha)\}\le\alpha$.

\begin{remark}[Unequal cheap-source costs]
\label{rmk:unequal-costs}
Under equal cheap-source costs the selected source
$j_t^\lambda\in\argmin_j\hath_{t}(j)$ does not depend on $\lambda$, the routed
loss is monotone in the scalar score $\min_j\hath_{t}(j)$, and
Theorem~\ref{thm:offline-fixed-price-pac} certifies the price selected over the
continuum $[0,\infty]$ with the monotone bound \eqref{eq:hoeffding-ucb} at level
$\alpha$. Under
unequal costs the selected source
$j_t^\lambda\in\argmin_j\{c_t(j)+\lambda\hath_{t}(j)\}$ varies with $\lambda$, so
source switching can make $L_T(\lambda)$ non-monotone and the single-point
argument no longer applies. One then certifies a finite price grid $\Lambda$
with the uniform bound \eqref{eq:hoeffding-ucb-uniform}---equivalently, replaces
$\alpha$ by $\alpha/|\Lambda|$ in \eqref{eq:hoeffding-ucb}---and
Corollary~\ref{cor:all-prices} bounds the grid size needed to cover the
continuum.
\end{remark}

Betting-based confidence sequences can also be used if the calibration stream
is reused while expanding the candidate price set.

\section{Not Very Meaningful Results}
\label{app:not-very-meaningful}

The following observation is included only to show that a continuum of prices
can be reduced to a finite policy class on a fixed finite dataset.
It is relevant only under unequal cheap-source costs, where source selection
varies with $\lambda$; under the equal-cost setting of the main text
Theorem~\ref{thm:offline-fixed-price-pac} already certifies the
continuum-selected price without it. It is not a main contribution: the resulting confidence penalty may be
larger than that of a deliberately chosen price grid, and it does not remove
the uniform-certification cost.

\subsection{Continuous Prices and Breakpoint Enumeration}
\label{sec:breakpoints}

For each item $t$, set $\hath_t(E)=0$ and $\hath_t(j)=\hath_{t}(j)$.
The action selected by a fixed price is the lower envelope of the $k+1$ lines
\[
    c_t(a)+\lambda\hath_t(a),
    \qquad a\in\{E,1,\ldots,k\}.
\]
The action can change only when two of these lines cross.

\begin{corollary}[Uniform certification over all prices]
\label{cor:all-prices}
Fix a bounded interval $[0,\lambda_{\max}]$ and include the expert-only policy
as an additional candidate.
Let $\Pi_{\lambda}$ be the fixed-price policy induced by the unique minimizer
\[
    a_t^\lambda\in\argmin_{a\in\{E,1,\ldots,k\}}
    \{c_t(a)+\lambda\hath_t(a)\}
\]
on the union of the target and calibration items.
The number of distinct induced policies over
$\lambda\in[0,\lambda_{\max}]$ at which these minimizers are unique is at most
\begin{equation}
    N_{\mathrm{br}}
    \le
    1+(T+m)\binom{k+1}{2}.
    \label{eq:breakpoint-count}
\end{equation}
Therefore the finite-policy uniform guarantee holds over all
\(\lambda\) with unique minimizers after replacing $|\Lambda|$ in
\eqref{eq:hoeffding-ucb-uniform} by $N_{\mathrm{br}}$. Under equal cheap-source
costs this enumeration is unnecessary: source selection does not depend on
$\lambda$, $L_T$ is monotone, and Theorem~\ref{thm:offline-fixed-price-pac}
already certifies the continuum-selected price with the monotone bound
\eqref{eq:hoeffding-ucb}.
\end{corollary}

\begin{proof}
For a fixed item, the selected action is constant between consecutive crossing
points of pairs of lines
$c_t(a)+\lambda\hath_t(a)$.
There are at most $\binom{k+1}{2}$ pairwise crossings per item.
Across $T+m$ target and calibration items, there are therefore at most
\[
    B=(T+m)\binom{k+1}{2}
\]
crossing values, counting multiplicity.
These crossing values partition $[0,\lambda_{\max}]$ into at most $B+1$ open
intervals. Within each open interval the entire vector of decisions on target
and calibration items is fixed.
Thus the number of distinct induced policies with unique minimizers is at most
\(B+1\).
Choose one representative price from each distinct induced policy and apply the
finite-policy Hoeffding union bound \eqref{eq:hoeffding-ucb-uniform} to those
representatives. Every \(\lambda\) with unique minimizers induces one of these
representative policies, so the same uniform guarantee holds over all such
prices.
\end{proof}

\subsection{Explicit Cost Accounting}

This accounting is useful for implementation, but it is not central to the
statistical guarantee.
The main distinction is between deployment cost, development-label cost, and
audit or correction cost.

\paragraph{Deployment labeling cost.}
For a fixed offline price $\lambda$, the average deployment cost on the target
pool is exactly $C_T(\lambda)$ from \eqref{eq:L-C-lambda}, that is,
$\frac1T\sum_{t=1}^T[D_t^\lambda c_{t,E}+(1-D_t^\lambda)c_{t,j_t^\lambda}]$.
This is the cost optimized in \eqref{eq:certified-price-selection}.
If cheap predictions have already been precomputed at no marginal deployment
cost, set $c_{t,j}=0$.
If calling a model has a per-token, per-image, or per-query cost, include that
cost in $c_{t,j}$.

\paragraph{Offline development cost.}
If $m_{\mathrm{train}}$ expert labels are used to train $\hath$ and
$m_{\mathrm{cal}}$ expert labels are used to certify the fixed price, the
development cost is
\begin{equation}
    C^{\mathrm{dev}}
    =
    \sum_{i\in I_{\mathrm{train}}} c_{i,E}
    +
    \sum_{i\in I_{\mathrm{cal}}} c_{i,E}
    +
    \textnormal{cheap-source costs incurred on development items}.
    \label{eq:development-cost}
\end{equation}
This cost may be treated as sunk if the labeled development data already exist,
but it should be included when comparing end-to-end data-curation pipelines.

\paragraph{Audit-or-correction cost.}
In the offline setting, calibration labels play the role that audits play
online.
If calibration items are part of the target pool and are corrected to expert
labels in the released dataset, then there is no duplicate expert cost for
those items.
The total realized end-to-end cost can be written as
\begin{equation}
    C_T^{\mathrm{total}}(\lambda)
    =
    \frac1T\sum_{t=1}^T
    \left[
        (1-D_t^\lambda)c_{t,j_t^\lambda}
        +
        \ind{D_t^\lambda\;\textnormal{or}\;t\in I_{\mathrm{cal}}}c_{t,E}
    \right]
    + C^{\mathrm{train}}/T,
    \label{eq:total-cost}
\end{equation}
where $C^{\mathrm{train}}$ denotes expert-labeling cost used only for proxy
training and not for final target labels.
This formula separates expert labels used for final deferral from expert
labels used for statistical certification.

\paragraph{Online audit cost.}
For Algorithm~\ref{alg:online-audited}, the conditional expected round-$t$
cost under audit-and-correct is
\[
    \E[C_t\mid\calG_t]
    =
    D_t+(1-D_t)p_t .
\]
This identity isolates the extra expert cost paid to obtain online feedback;
it is not a cost-regret guarantee.

\bibliographystyle{unsrt}
\bibliography{ref}

\end{document}
